---
title: "Cleaning and Processing Data"
author: "Nikhil Kalathil"
date: "5/11/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include = FALSE}
#install.packages('ggmap', 'RJSONIO')
library(tidyverse)
library(ggmap)
library(leaflet)
library(leaflet.extras)
library(htmltools)
library(htmlwidgets)
library(RJSONIO)
library(readxl)
library(widgetframe)
```

This document provides a procedure for cleaning, geocoding, and formatting data for ultimate mapping. The output should be a series of RDS files that can then be read by the mapping file. 

# Geolocating

## Swabs

We start by loading our data. 
```{r}
us_swabs_hq <- read_xlsx("swabs_us.xlsx")
```


We then begin the process of geocoding. We will use [Google's geolocating service](https://developers.google.com/maps/documentation/geocoding/intro) to process our geolocation requests. To use this service, we need to get an [API key](https://developers.google.com/maps/documentation/geocoding/get-api-key)

```{r, echo = FALSE, Include = FALSE}
api_key <- c("YOUR_KEY")
```

We define our function, which will take an address as an input and output a latitude and longitude result. 

```{r}
geocodeAddress <- function(address) {
  require(RJSONIO)
  url <- "https://maps.googleapis.com/maps/api/geocode/json?address="
  url <- URLencode(paste(url, address, sep = ""))
  url <- URLencode(paste(url, "&key=", api_key, sep = ""))
  x <- fromJSON(url, simplify = FALSE)
  print(x$status)
  if (x$status == "OK") {
    out <- c(x$results[[1]]$geometry$location$lng,
             x$results[[1]]$geometry$location$lat,
             x$results[[1]]$formatted_address)
  } else {
    out <- NA
  }
  Sys.sleep(0.2)  # API only allows 5 requests per second
  out
}
```

We now clean and prepare our data for geocoding. 

```{r}
us_swabs_hq <- us_swabs_hq %>% 
  rename(Location = Headquarters) %>% 
  mutate(address = paste(Company, Location, sep = ", ")) %>% 
  mutate(broad_product = "Swabs", purpose = "Testing", loc_desc = "Company HQ") %>% 
  mutate(specific_product = case_when(
    Company %in% c("Copan","Becton, Dickinson and Company (BD)", "Fisher Healthcare") ~ "Nasopharyngeal and Oropharyngeal Swabs", 
    Company %in% c("Quidel") ~ "Nasopharyngeal Swabs", 
    Company %in% c("Puritan Medical Products") ~ "Nasopharyngeal, Oropharyngeal, and Other Swabs"
  ), 
  product_details = paste(`Nasopharyngeal Swabs`, `Oropharyngeal Swabs`, `Other Acceptable Sterile Flocked Swabs`, sep = ", ")) %>% 
  rename(employees = "Number of Employees", sales = "Annual Sales")
```

Now we loop through the addresses to get the latitude and longitude of each address and add it to the original address data frame in the  new columns lat and long. 

```{r}
origAddress <- us_swabs_hq
```


```{r}
for(i in 1:nrow(origAddress))
{
  result <- geocodeAddress(origAddress$address[i])
  origAddress$long[i] <- as.numeric(result[1])
  origAddress$lat[i] <- as.numeric(result[2])
  origAddress$form_address[i] <- as.character(result[3])

}
```


Save this as a new object to prepare for leaflet plotting. In doing so we want to define as identifying factors for this layer as possible. We want our final object to have the following format: 

* Company Name
* Country of Ownership / Headquarters
* Location Type (HQ, subsidiary, etc.) 
* For Each Facility
  * Address
  * Purpose (testing, PPE, etc)
  * Broad Product Type (masks, gowns, swabs, etc)
  * Specfic Product (Nasopharyngeal, ASTM 1/2/3, etc.)
  * Product Details (Mm dimensions, nonwoven fabrics etc)
  * Capacity
  * Number of Employees (if available)
  * Annual Sales (if available)

```{r}
geocoded_swabs <- origAddress %>% 
  mutate(ownership = case_when(
    Company == "Copan" ~ "Italy", 
    TRUE ~ "USA"), 
    capacity = NA_character_) %>% 
  select(company = Company, ownership, loc_desc, address, purpose, broad_product, specific_product, product_details, capacity, employees, sales, lat, long)
```

## Non-Woven Fabrics

We then add another layer of data to test our layering. 

```{r}
top_nonwoven <- read_xlsx("nonwoven_us.xlsx")
```

```{r}
top_nonwoven <- top_nonwoven %>%
  rename(Company = `Company Name`) %>% 
  mutate(address = paste(Company, Location, sep = ", ")) %>% 
  mutate(broad_product = "ASTM Level 2 +", specific_product = "Nonwoven Fabrics", product_details = "25+ GSM Fabric", purpose = "Surgical Masks", loc_desc = "Company HQ") %>% 
  rename(sales = 'Estimated Annual Revenue')
```

Note: Nonwoven fabrics are also used in gowns. It is unclear how we want to deal with this (i.e stack? seperate?), and will depend on how the data look when combined with additional layers. 

```{r}
for (i in c(1,4,5,8,9,10))
{
  top_nonwoven$address[i] <- paste(top_nonwoven$address[i], "USA", sep = ", ")
}
```


```{r}
origAddress <- top_nonwoven
```



```{r}
for(i in 1:nrow(origAddress))
{
  result <- geocodeAddress(origAddress$address[i])
  origAddress$long[i] <- as.numeric(result[1])
  origAddress$lat[i] <- as.numeric(result[2])
  origAddress$form_address[i] <- as.character(result[3])
}
```

```{r}
geocoded_nonwoven <- origAddress %>% 
  mutate(ownership = sub('.*,\\s*', '', address), 
         capacity = NA_character_, 
         employees = NA_real_) %>% 
  select(company = Company, ownership, loc_desc, address, purpose, broad_product, specific_product, product_details, capacity, employees, sales, lat, long)
```

# Format for maps


## Prepare our Data

```{r}
df_for_maps <- bind_rows(geocoded_swabs, geocoded_nonwoven)
```

We then prepare the individual data frames that house individual layers and contain relevant popup infromation. In this case we only have two sublayers: swabs and non-woven fabrics. Since we intend on adding many layers, we create a function to do this. In this document we will seperately call the function for the two layers of our map. 

```{r}
prepare_for_maps <- function(name, df, title) {
  test <- as.character(title)
  name <- df %>% 
    mutate(layerId = paste(test, row_number(), sep = '.'),
                      popup = paste("Company Name:",
                                    df$company, "<br>",
                                    "Country of Ownership:",
                                    df$ownership, "<br>",
                                    "Location Type:", 
                                    df$loc_desc, "<br>",
                                    "Address:", 
                                    df$address, "<br>",
                                    "Purpose:", 
                                    df$purpose, "<br>",
                                    "Broad Product Type:", 
                                    df$broad_product, "<br>",
                                    "Specfic Product:", 
                                    df$specific_product, "<br>",
                                    "Product Details:",
                                    df$product_details, "<br>",
                                    "Capacity:", 
                                    df$capacity, "<br>",
                                    "Number of Employees:", 
                                    df$employees, "<br>",
                                    "Annual Sales:", 
                                    df$sales, "<br>"
                                    ))
  return(name)
}
```

```{r}
swabs <- prepare_for_maps(swabs, geocoded_swabs, 'swabs')
```

```{r}
nonwoven <- prepare_for_maps(nonwoven, geocoded_nonwoven, 'nonwoven')
```

## Save for outputs 

We now save our outputs to the locations that our other files can draw from. 

### For mapping output only

```{r}
saveRDS(df_for_maps, "Data/df_for_maps.rds")
saveRDS(swabs, "Data/swabs.rds")
saveRDS(nonwoven, "Data/nonwoven.rds")
```

### For shiny integration and searching 

```{r}
saveRDS(df_for_maps, "Leaflet_Searching/Data/df_for_maps.rds")
saveRDS(swabs, "Leaflet_Searching/Data/swabs.rds")
saveRDS(nonwoven, "Leaflet_Searching/Data/nonwoven.rds")
```

