---
title: "thomasnet_cleaning_functions"
author: "Nikhil Kalathil"
date: "6/18/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include == FALSE }
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(ggthemes)
library(tm)
library(here)
library(ggrepel)
library(lubridate)
library(ggnewscale)
library(readxl)
library(htmltools)
library(htmlwidgets)
library(RJSONIO)
```

# Define Directory

```{r}

box_dir <- "C:/Users/Nikhil Kalathil/Box/COVID 19 Master Folder/Data/Tests/Thomasnet Pulls/"

```

```{r}
box_here <- function(file) {
  paste(box_dir, file, sep = "")
}
```

# Read and Bind

```{r}
read_bind <- function(date) {
  
  
  file_suffix <- str_replace_all(date, "\\_", "")
  
  end_prods <- readRDS(paste(box_dir, date, "/test_end_", file_suffix, ".RDS", sep ="")) %>% 
      group_by(company) %>% 
    mutate(tal = seq(n())) %>% 
    mutate(specific_product = case_when(
      tal == 2 ~ "Covid-19 Test Kits", 
      TRUE ~ specific_product)) %>% 
    filter(tal < 2) %>% 
    select(-tal) %>% 
    mutate(antibody = case_when(
        specific_product == "Covid-19 Test Kits" & (str_detect(desc, "IgG") | str_detect(desc, "IgM") | str_detect(desc, "antibody") | str_detect(desc, "Antibody") | str_detect(desc, "serological")) ~ 1, 
      TRUE ~ 0), 
      antigen = case_when(
        specific_product == "Covid-19 Test Kits" & (str_detect(desc, "IgA") | str_detect(desc, "antigen") | str_detect(desc, "Antigen")) ~ 1, 
      TRUE ~ 0),
      PCR = case_when(
        specific_product == "Covid-19 Test Kits" & str_detect(desc, "PCR") ~ 1, 
      TRUE ~ 0), 
      unknown = case_when(
       specific_product == "Covid-19 Test Kits" & antibody == 0 & antigen == 0 & PCR == 0 ~ 1, 
       TRUE ~ 0
        )
    ) %>% 
    ungroup() %>% 
      filter(str_detect(desc, "test") | str_detect(desc, "medical") | str_detect(desc, "detection"))
  
  int_prods <- readRDS(paste(box_dir, date, "/test_int_", file_suffix, ".RDS", sep =""))
  
    df <- bind_rows(end_prods, int_prods) 
    
    return(df)
}
```

```{r}
read_reagents <- function(date) {
  
   file_suffix <- str_replace_all(date, "\\_", "")
   
   reagents <- readRDS(paste(box_dir, date, "/reagents_full_", file_suffix, ".RDS", sep ="")) 
   
   return(reagents)
   
}
```

```{r}
read_other <- function(date) {
  
   file_suffix <- str_replace_all(date, "\\_", "")
   
   other <- readRDS(paste(box_dir, date, "/test_other_", file_suffix, ".RDS", sep ="")) 
   
   return(other)
   
}
```



# Define Suppliers

```{r}
suppliers <- function(data){ 
  data %>% 
    mutate(broad_loc = case_when(
    str_detect(loc_desc, "Manufacturer\\*") ~ "Primary Manufacturer", 
    str_detect(loc_desc, "Manufacturer") & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) ~ "Secondary Manufacturer",
    str_detect(loc_desc, "Distributor") | str_detect(loc_desc, "Manufacturers' Rep*") ~ "Distributor", 
    str_detect(loc_desc, "Manufacturer", negate = TRUE) & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) & 
      str_detect(loc_desc, "Distributor", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep*", negate = TRUE) ~ "Other"))
  }
```

# Put Together

```{r}
clean_prods <- function(date){
  
  raw <- read_bind(date)
  
  file_suffix <- str_replace_all(date, "\\_", "")
  
  raw %>% 
    suppliers() %>%
      mutate(date = mdy(file_suffix))
    
    
}
```

```{r}
clean_reagents <- function(date){ 
  raw <- read_reagents(date)
  
  file_suffix <- str_replace_all(date, "\\_", "")
  
  raw %>% 
    suppliers() %>%
      mutate(date = mdy(file_suffix))
  
  }
```

```{r}
clean_other <- function(date){ 
  raw <- read_other(date)
  
  file_suffix <- str_replace_all(date, "\\_", "")
  
  raw %>% 
    suppliers() %>%
      mutate(date = mdy(file_suffix))
  
  }
```


# Combine Datasets

## Combining datasets

```{r}
thomas_files <- list()

file_list <- list.files(box_dir)

i <- 1

for (file in 1:length(file_list)) {
  
  filename <- file_list[file]
  
  print(filename)
  
  thomas_files[[file]] <- clean_prods(filename)
  
  i <- i+1
}
```
```{r}
test_prods <- bind_rows(thomas_files[[1]], thomas_files[[2]])
```


```{r, eval = FALSE}
test_prods <- bind_rows(thomas_files[[1]], thomas_files[[2]])

for (i in 3:length(thomas_files)) {
  
  test_prods <- bind_rows(test_prods, thomas_files[[i]])
  
  i <- i+1
}
```

```{r}
reagents_files <- list()

file_list <- list.files(box_dir)

i <- 1

for (file in 1:length(file_list)) {
  
  filename <- file_list[file]
  
  print(filename)
  
  reagents_files[[file]] <- clean_reagents(filename)
  
  i <- i+1
}
```

```{r}
reagents <- bind_rows(reagents_files[[1]], reagents_files[[2]])
```

```{r}
other_files <- list()

file_list <- list.files(box_dir)

i <- 1

for (file in 1:length(file_list)) {
  
  filename <- file_list[file]
  
  print(filename)
  
  other_files[[file]] <- clean_other(filename)
  
  i <- i+1
}
```

```{r}
other <- bind_rows(other_files[[1]], other_files[[2]])
```


```{r}
box_dir <- "C:/Users/Nikhil Kalathil/Box/COVID 19 Master Folder/Data/Tests/"
```

```{r}
saveRDS(test_prods, box_here("thomasnet_totals/test_prods.RDS"))
```

```{r}
saveRDS(other, box_here("thomasnet_totals/other_prods.RDS"))
```

```{r}
saveRDS(reagents, box_here("thomasnet_totals/reagent_prods.RDS"))
```


# Structure and Graph

```{r}
test_struc <- test_prods %>% 
  mutate(broad_loc = case_when(
    str_detect(broad_loc, "Manuf") ~ "Manufacturer", 
    str_detect(broad_loc, "Dist") ~ "Distributor",
    TRUE ~ "Other/Unknown"
  ), 
  broad_loc = case_when(
    str_detect(desc, fixed("distributor", ignore_case = TRUE)) & str_detect(desc, fixed("manufacturer", ignore_case = TRUE), negate = TRUE) ~ "Distributor", 
    TRUE ~ broad_loc
  )) %>%  
    group_by(specific_product, company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

```{r}
reagents_struc <- reagents %>% 
   mutate(broad_loc = case_when(
    str_detect(broad_loc, "Manuf") ~ "Manufacturer", 
    str_detect(broad_loc, "Dist") ~ "Distributor",
    TRUE ~ "Other/Unknown"
  ), 
  broad_loc = case_when(
    str_detect(desc, fixed("distributor", ignore_case = TRUE)) & str_detect(desc, fixed("manufacturer", ignore_case = TRUE), negate = TRUE) ~ "Distributor", 
    TRUE ~ broad_loc
  )) %>%  
    group_by(specific_product, company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

```{r}
other_struc <- other %>% 
   mutate(broad_loc = case_when(
    str_detect(broad_loc, "Manuf") ~ "Manufacturer", 
    str_detect(broad_loc, "Dist") ~ "Distributor",
    TRUE ~ "Other/Unknown"
  ), 
  broad_loc = case_when(
    str_detect(desc, fixed("distributor", ignore_case = TRUE)) & str_detect(desc, fixed("manufacturer", ignore_case = TRUE), negate = TRUE) ~ "Distributor", 
    TRUE ~ broad_loc
  )) %>%  
    group_by(specific_product, company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```



## Differentiating by Supplier Type
```{r}
my_pal <- c(brewer.pal(4, "Set3")[4], brewer.pal(4, "Paired")[2])
```


```{r}
sup1 <- test_struc %>% 
  group_by(date, broad_product, specific_product, broad_loc) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos_loc = case_when(
    broad_loc == "Manufacturer" ~ 1, 
    broad_loc == "Distributor" ~ 2, 
    broad_loc == "Other/Unknown" ~ 3
  )) %>% 
  filter(broad_loc != "Other/Unknown") %>% 
  mutate(specific_product = reorder(specific_product, n), 
         broad_loc = reorder(broad_loc, -pos_loc)) %>% 
  ggplot(aes(date, n, fill = broad_loc, group = broad_loc)) +
  geom_area(position = "stack", show.legend = FALSE, color = "Black", alpha = 0.8 ) +
  geom_point(shape =21, color = "Black", alpha = 0.7, size = 1 ,position = "stack") +
  scale_fill_manual(values = my_pal) + 
  facet_wrap(~reorder(specific_product, n)) +
  labs(title = "Number of Suppliers by Product and Thomasnet Supplier Type", subtitle = "Thomasnet 05/30/20 - 11/02/20", y = "Unique Thomasnet Suppliers", x = "", fill = "Supplier Type") + 
  theme_bw()

sup1
```
# Base Graphs

```{r}
thomas_graph <- test_struc %>% 
  filter(!specific_product %in% c("Reagents (All)", "Plastics Contract Manufacturing"), broad_loc == "Manufacturer" ) %>% 
  group_by(date, broad_product, specific_product) %>% 
  summarise(antigen = sum(antigen, na.rm = TRUE), antibody = sum(antibody, na.rm = TRUE), PCR = sum(PCR, na.rm = TRUE), unknown = sum(unknown, na.rm = TRUE), n = n()) %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Covid-19 Test Kits" ~ 1, 
    specific_product == "Other Test Kits" ~ 2, 
    specific_product == "Oropharyngeal Swabs" ~ 4, 
    specific_product == "Nasopharyngeal Swabs" ~ 5, 
    specific_product == "RNA Extraction Machine" ~ 3,
    specific_product == "Nucleotides" ~ 6,
    specific_product == "Reagents (All)" ~ 7, 
    specific_product == "Plastics Contract Manufacturing" ~ 8, 
    specific_product == "Viral Transport Medium (VTM)" ~ 9 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos)) 
```
```{r}
covid_tests_graph <- test_struc %>% 
  filter(specific_product != "NA", broad_loc == "Manufacturer", specific_product == "Covid-19 Test Kits" )
```


```{r}
reagents_graph <- reagents_struc %>% 
  filter(specific_product != "NA", broad_loc == "Manufacturer" ) %>% 
  group_by(date, broad_product, specific_product) %>% 
  count()  %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Reagents" ~ 1, 
    specific_product == "Bacteriological Reagents" ~ 4, 
    specific_product == "Biochemical Reagents" ~ 3, 
    specific_product == "Diagnostic Reagents" ~ 2, 
    specific_product == "Serological Reagents" ~ 6,
    specific_product == "Virological Reagents" ~ 5,
    specific_product == "Reagent Bottles" ~ 7
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos)) 
```

```{r}
other_graph <- other_struc %>% 
  filter(specific_product != "NA", broad_loc == "Manufacturer" ) %>% 
  group_by(date, broad_product, specific_product) %>% 
  count()  %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Vials" ~ 1, 
    specific_product == "Pipettes" ~ 2, 
    specific_product == "Pipette Tips" ~ 3, 
    specific_product == "Vortex Mixers" ~ 4, 
    specific_product == "Microcentrifuges" ~ 5, 
    specific_product == "Glass Vials" ~ 6
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos)) 
```


```{r}
fig_1 <- thomas_graph %>% 
  ggplot(aes(specific_product, n, fill = specific_product, label = n)) +
  geom_col(position = "stack", show.legend = FALSE) + 
  geom_label(show.legend = FALSE) + 
  scale_fill_brewer(palette = "Set3") +
  labs(title = "Number of Potential Domestic Manufacturing Entities by Product Type", subtitle = "Source: Thomasnet, 1/7/2021. Manufacturers Self-Identifying as: \nProducing Potentially Relevant Products for COVID-19 Tests", x = "", y = "Unique Manufacturing Entities") + 
  coord_flip() + 
  theme_bw()
```

```{r}
fig_2 <- reagents_graph %>% 
  ggplot(aes(specific_product, n, fill = specific_product, label = n)) +
  geom_col(position = "stack", show.legend = FALSE) + 
  geom_label(show.legend = FALSE) + 
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Number of Potential Domestic Manufacturing Entities by Product Type", subtitle = "Source: Thomasnet, 1/7/2021. Manufacturers Self-Identifying as: \nProducing Reagents Potentially Relevant to COVID-19 Tests", x = "", y = "Unique Manufacturing Entities") + 
  coord_flip() + 
  theme_bw()
```

```{r}
fig_3 <- other_graph %>% 
  ggplot(aes(specific_product, n, fill = specific_product, label = n)) +
  geom_col(position = "stack", show.legend = FALSE) + 
  geom_label(show.legend = FALSE) + 
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Number of Potential Domestic Manufacturing Entities by Product Type", subtitle = "Source: Thomasnet, 1/7/2021. Manufacturers Self-Identifying as: \nProducing Other Products Potentially Relevant to COVID-19 Tests", x = "", y = "Unique Manufacturing Entities") + 
  coord_flip() + 
  theme_bw()
```


# Mapping

```{r}
test_map <- test_struc %>% 
  filter(broad_loc == "Manufacturer" )
```

```{r}
other_map <- other_struc %>% 
  filter(broad_loc == "Manufacturer")
```

```{r}
test_addresses <- test_map %>% 
  ungroup() %>% 
  distinct(company, location) %>% 
  mutate(address = paste(company, location, sep = ", "))
```

```{r}
other_addresses <- other_map %>% 
  ungroup() %>% 
  distinct(company, location) %>% 
  mutate(address = paste(company, location, sep = ", "))
```

# Geocoding


```{r, echo = FALSE, Include = FALSE}
api_key <- c("AIzaSyA1pwzK3BaX7_um-_TUrS7aGfCHQvp68b8")
```

We define our function, which will take an address as an input and output a latitude and longitude result. 

```{r}
geocodeAddress <- function(address) {
  require(RJSONIO)
  url <- "https://maps.googleapis.com/maps/api/geocode/json?address="
  url <- URLencode(paste(url, address, sep = ""))
  url <- URLencode(paste(url, "&key=", api_key, sep = ""))
  x <- fromJSON(url, simplify = FALSE)
  print(x$status)
  if (x$status == "OK") {
    out <- c(x$results[[1]]$geometry$location$lng,
             x$results[[1]]$geometry$location$lat,
             x$results[[1]]$formatted_address)
  } else {
    out <- NA
  }
  Sys.sleep(0.2)  # API only allows 5 requests per second
  out
}
```

```{r, include = FALSE}
for(i in 1:nrow(test_addresses))
{
  result <- geocodeAddress(test_addresses$address[i])
  test_addresses$long[i] <- as.numeric(result[1])
  test_addresses$lat[i] <- as.numeric(result[2])
  test_addresses$form_address[i] <- as.character(result[3])

}
```

```{r, include = FALSE}
for(i in 1:nrow(other_addresses))
{
  result <- geocodeAddress(other_addresses$address[i])
  other_addresses$long[i] <- as.numeric(result[1])
  other_addresses$lat[i] <- as.numeric(result[2])
  other_addresses$form_address[i] <- as.character(result[3])

}
```


```{r}
geocoded_test_maps <- left_join(test_map, test_addresses) %>% 
  ungroup()
```
```{r}
geocoded_other_maps <- left_join(other_map, other_addresses)
```

```{r}
geocoded_tests <- bind_rows(geocoded_test_maps, geocoded_other_maps) %>% 
  group_by(company, location) %>% 
  mutate(first_date = min(date), 
         last_date = max(date)) %>% 
  ungroup()
```

```{r}
saveRDS(geocoded_tests, box_here("thomasnet_totals/geocoded_tests.RDS"))
```

```{r}
unique_geocoded_tests <- geocoded_tests %>% 
  filter(date == max(date)) 

unique_geocoded_tests <- anti_join(unique_geocoded_tests, geocoded_tests, by = c("company", "location")) %>% 
  bind_rows(unique_geocoded_tests)
  
```

```{r}
unique_geocoded_tests <- unique_geocoded_tests %>% 
  mutate(Primers = case_when(str_detect(desc, fixed("primer", ignore_case = TRUE)) == 1 ~ 1), 
         Probes = case_when(str_detect(desc, fixed("probe", ignore_case = TRUE)) == 1 ~ 1), 
         master_mix = case_when(str_detect(desc, fixed("master mix", ignore_case = TRUE)) == 1 & str_detect(desc, fixed("green master mix", ignore_case = TRUE)) != 1 ~ 1), 
         Detection = case_when(str_detect(desc, fixed("detection", ignore_case = TRUE)) == 1 ~ 1)) %>% 
  mutate(saliva_direct = case_when(
    Primers == 1 | Probes == 1 | master_mix == 1 | Detection == 1 ~ 1
  ))
```

```{r}
prepare_for_maps <- function(df) {
  df %>% 
    mutate(layerId = paste(specific_product, row_number(), sep = '.'),
                      popup = paste("<strong>Company Name:</strong>",
                                    df$company, "<br>",
                                    "<strong>Address:</strong>", 
                                    df$address, "<br>",
                                    "<strong>Broad Product:</strong>", 
                                    df$broad_product, "<br>",
                                    "<strong>Specific Product:</strong>", 
                                    df$specific_product, "<br>",
                                    "<strong>(TN) Sales:</strong>", 
                                    df$sales, "<br>",
                                    "<strong>(TN) Employees:</strong>", 
                                    df$employees, "<br>",
                                    "<strong>(TN) Date Founded:</strong>",
                                    df$date_founded, "<br>",
                                    "<strong>Thomas Verified:</strong>",
                                    df$thomas_ver, "<br>",
                                    "<strong>Thomasnet Covid-19 Response:</strong>",
                                    df$covid_19, "<br>",
                                    "<strong>Thomasnet Description:</strong>", 
                                    df$desc, "<br>",
                                    "<strong>Antibody Test:</strong>", 
                                    df$antibody, "<br>",
                                    "<strong>Antigen Test:</strong>", 
                                    df$antigen, "<br>",
                                    "<strong>PCR Test:</strong>", 
                                    df$PCR, "<br>", 
                                    "<strong>First Date in Data:</strong>", 
                                    df$first_date, "<br>", 
                                    "<strong>Last Date in Data:</strong>", 
                                    df$last_date, "<br>",
                                    "<strong>Potentially Useful in Saliva Direct Test:</strong>", 
                                    df$saliva_direct, "<br>"
                                    ), 
                      group = specific_product)

}
```

We first use this function to set up our individual data layers for mapping. 

```{r}
tests_maps <- prepare_for_maps(unique_geocoded_tests)
```

# Mapping 

```{r}
tests_maps %>% 
  saveRDS(box_here("thomasnet_totals/tests_geocoded.RDS"))
```

```{r}
tests_maps %>% saveRDS(here("/domestic_manufacturers/tests_geocoded.RDS"))
```

# Saliva Direct BoM

Step 1: Manual search for various entries

## Thomasnet Suppliers

Results for: Primer, Probe, Master Mix, Detection 

```{r}
saliva_direct <- geocoded_tests %>% 
  mutate(Primers = case_when(str_detect(desc, fixed("primer", ignore_case = TRUE)) == 1 ~ 1), 
         Probes = case_when(str_detect(desc, fixed("probe", ignore_case = TRUE)) == 1 ~ 1), 
         master_mix = case_when(str_detect(desc, fixed("master mix", ignore_case = TRUE)) == 1 & str_detect(desc, fixed("green master mix", ignore_case = TRUE)) != 1 ~ 1), 
         Detection = case_when(str_detect(desc, fixed("detection", ignore_case = TRUE)) == 1 ~ 1)) %>% 
  filter(Primers == 1 | Probes == 1 | master_mix == 1 | Detection == 1)
```

```{r}
saliva_direct %>% 
  filter(date == max(date)) %>%
  write_csv(box_here("saliva_direct_potential_suppliers.csv"))
```

```{r}
saliva_direct_primers <- saliva_direct %>% 
  filter(Primers == 1) %>% 
  mutate(product = "Primers")

saliva_direct_probes <- saliva_direct %>% 
  filter(Probes == 1) %>% 
  mutate(product = "Probes")

saliva_direct_master_mix <- saliva_direct %>% 
  filter(master_mix == 1) %>% 
  mutate(product = "Master Mix")

saliva_direct_detection <- saliva_direct %>% 
  filter(Detection == 1) %>% 
  mutate(product = "Detection")

saliva_direct_maps <- bind_rows(saliva_direct_primers, saliva_direct_probes) %>% 
  bind_rows(saliva_direct_master_mix) %>% 
  bind_rows(saliva_direct_detection)

rm(saliva_direct_primers, saliva_direct_probes, saliva_direct_master_mix, saliva_direct_detection)
```


```{r}
saliva_direct_graph <- saliva_direct %>% 
  group_by(date) %>% 
  summarise(Primers = sum(Primers, na.rm = TRUE), Probes = sum(Probes, na.rm = TRUE), master_mix = sum(master_mix, na.rm = TRUE), Detection = sum(Detection, na.rm = TRUE)) %>% 
  pivot_longer(cols = -date, names_to = "product", values_to = "n") %>% 
  mutate(product = if_else(product == "master_mix", "Master Mix", product))
```
```{r}
fig_4 <- saliva_direct_graph %>% 
  filter(date == max(date)) %>% 
  ggplot(aes(reorder(product, n), n, fill = product, label = n)) +
  geom_col(position = "stack", show.legend = FALSE) + 
  geom_label(show.legend = FALSE) + 
  scale_fill_brewer(palette = "Set2") +
  labs(title = "Number of Potential Domestic Manufacturing Entities by Product Type", subtitle = "Source: Thomasnet, 1/11/2021. Manufacturers Self-Identifying as: \nProducing Products Potentially Relevant to Saliva Direct COVID-19 Tests ", x = "", y = "Unique Manufacturing Entities") + 
  coord_flip() + 
  theme_bw()
```


## Saliva Direct Labs

```{r}
sd_labs <- read_xlsx(box_here("saliva_direct_labs.xlsx")) 
```

```{r}
sd_labs <- sd_labs %>% 
  mutate(contact = str_trim(contact), 
         product = "Saliva Direct Lab")
```

```{r, include = FALSE}
for(i in 1:nrow(sd_labs))
{
  result <- geocodeAddress(sd_labs$address[i])
  sd_labs$long[i] <- as.numeric(result[1])
  sd_labs$lat[i] <- as.numeric(result[2])
  sd_labs$form_address[i] <- as.character(result[3])

}
```

```{r}
prepare_for_maps_sd_labs <- function(df) {
  df %>% 
    mutate(layerId = paste(product, row_number(), sep = '.'),
                      popup = paste("<strong>Lab Name:</strong>",
                                    df$company_name, "<br>",
                                    "<strong>Address:</strong>", 
                                    df$address, "<br>",
                                    "<strong>Contact:</strong>", 
                                    df$contact, "<br>",
                                    "<strong>Phone:</strong>", 
                                    df$phone, "<br>",
                                    "<strong>Email:</strong>", 
                                    df$email, "<br>",
                                    "<strong>Product:</strong>", 
                                    df$product, "<br>"
                                    ), 
                      group = product)

}
```

```{r}
prepare_for_maps_sd <- function(df) {
  df %>% 
    mutate(layerId = paste(product, row_number(), sep = '.'),
                      popup = paste("<strong>Company Name:</strong>",
                                    df$company, "<br>",
                                    "<strong>Address:</strong>", 
                                    df$address, "<br>",
                                    "<strong>Broad Product:</strong>", 
                                    df$broad_product, "<br>",
                                    "<strong>Specific Product:</strong>", 
                                    df$specific_product, "<br>",
                                    "<strong>(TN) Sales:</strong>", 
                                    df$sales, "<br>",
                                    "<strong>(TN) Employees:</strong>", 
                                    df$employees, "<br>",
                                    "<strong>(TN) Date Founded:</strong>",
                                    df$date_founded, "<br>",
                                    "<strong>Thomas Verified:</strong>",
                                    df$thomas_ver, "<br>",
                                    "<strong>Thomasnet Covid-19 Response:</strong>",
                                    df$covid_19, "<br>",
                                    "<strong>Thomasnet Description:</strong>", 
                                    df$desc, "<br>",
                                    "<strong>Antibody Test:</strong>", 
                                    df$antibody, "<br>",
                                    "<strong>Antigen Test:</strong>", 
                                    df$antigen, "<br>",
                                    "<strong>PCR Test:</strong>", 
                                    df$PCR, "<br>", 
                                    "<strong>First Date in Data:</strong>", 
                                    df$first_date, "<br>", 
                                    "<strong>Last Date in Data:</strong>", 
                                    df$last_date, "<br>"
                                    ), 
                      group = product)

}
```

```{r}
sd_labs <- prepare_for_maps_sd_labs(sd_labs) %>% 
  rename(company = company_name) %>% 
  select(company, address, lat, long, form_address, product, popup)
```

```{r}
sd_maps <- prepare_for_maps_sd(saliva_direct_maps) %>% 
    select(company, address, lat, long, form_address, product, popup)
```

```{r}
sd_maps <- bind_rows(sd_labs, sd_maps)
```

```{r}
sd_maps %>% saveRDS(here("/domestic_manufacturers/sd_geocoded.RDS"))
```

