---
title: "Cleaning and Analyzing Face Mask and Respirator Thomasnet Supplier Searches "
author: "Nikhil Kalathil"
date: "5/28/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include == FALSE }
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(ggthemes)
library(tm)
```


# Introduction

This document will clean and process data webscraped from Thomasnet to: 

* Differentiate product layers 
* Differentiate supply types
* Determine FDA compliance status 
* Determine distribution of COVID-19 resposne


## Preparing the Data 

We spend our first section preparing data that we have. 

### Face Masks and Respirators 

Our first task is to distinguish the difference in overlap between our "Face Masks" search and our" "Respirators" search. 

To do this we import both data sets, combine them, and then filter down to distinct company rows. 

```{r}
thomas_fm <- readRDS("Data/thomas_fm_05292020.RDS")

thomas_fm %>% 
  count() 
```

```{r}
thomas_resp <- readRDS("Data/thomas_resp_05292020.RDS")

thomas_resp %>% 
  count()
```

```{r}
thomas_data <- bind_rows(thomas_resp, thomas_fm) %>% 
  rename(search_prod = purpose, 
         broad_product = specific_product)
```

We find that we can identify unique entries based on a combination of `company, desc, location`. 

```{r}
thomas_data %>% 
  group_by(company, desc, location) %>% 
  count() %>% 
  group_by(n) %>% 
  count()
```

Surprisingly, we find that there are only 78 categories that overlapped between these searches! Once we analyze the actual supplier descriptions further it wil be interesting to see how topics differentiation between the respirator search query (as identified in the specific_product variable), and the face mask search. 

```{r}
thomas_double <- thomas_data %>% 
  group_by(company, desc) %>% 
  count() %>% 
  filter(n == 2) %>% 
  mutate(search_prod = "Face Masks and N95 Respirators", broad_product = "End Product") %>% 
  select(-n)
```

```{r}
thomas_clean <- anti_join(thomas_data, thomas_double, by = c("company", "desc")) %>% 
  bind_rows(thomas_double)
```


We now have: 

```{r}
thomas_clean %>% 
  group_by(search_prod) %>% 
  count()
```


We note that there are a few entries that have the same location but slightly different descriptions under the "face mask" search and under the "respirators" search. The degree to which these descriptions vary differs, but because they do differ, we leave them as separate rows in our data. 

Thus, there is a small amount of repitition in our data, and it is important to note that companies that produce "Face Masks and N95 Respirators" are companies that have the exact same description under both the face mask and respirators search.


### Further Cleaning


We now continue to clean this search file for analysis. In general, we can drop observations that do not have a body text. However, there are many observations that do not have sales or employees data, but do have interested data about production lines and product mixes. 

For example: 

```{r}
thomas_clean %>%  
  filter(company == "Safeguard 19") %>% 
  select(company, location, loc_desc, sales, employees, desc)
```

Specifically, we have interesting information in the description variable that we want to anayze further. Our first step is to drop totally missing observations, as we cannot get observations about them. We notice that there are a few rows with no text or. We also notice that Covid 19 and some other descriptors of interest are sometimes two words. 

```{r}
thomas_clean <- thomas_clean %>% 
  mutate(desc = str_replace(desc, fixed("covid 19", ignore_case = TRUE), "covid-19"), 
         desc = str_replace(desc, fixed("non woven", ignore_case = TRUE), "non-woven"), 
         desc = str_replace(desc, fixed("melt blown", ignore_case = TRUE), "melt-blown"),
         desc = str_replace(desc, fixed("3 ply", ignore_case = TRUE), "3-ply"),
         desc = str_replace(desc, fixed("3ply", ignore_case = TRUE), "3-ply"),
         desc = str_replace(desc, fixed("clean room", ignore_case = TRUE), "cleanroom") 
         ) %>% 
  filter(str_length(desc) > 2)
```


```{r}
thomas_clean$ID <- seq.int(nrow(thomas_clean))
```


### Structuring the Data

We now begin our process of structuring the data. Our ulimtate goal is to segment the combined respirator and face mask data into the following groups: 

End Products: 
* Respirators
* Face Masks
* Cloth Masks 

For this grouping, in the data we will define producers who can produce both respirators and face masks seperately. In maps, they will appear in both layers. 

Cloth masks are defined as companies that do not produce masks that meet any additional medical classifications.


```{r}
thomas_struc <- thomas_clean %>% 
  mutate(resp = case_when(
    str_detect(desc, fixed("respirator", ignore_case = TRUE)) | 
      str_detect(desc, fixed("N95", ignore_case = TRUE)) | 
      str_detect(desc, fixed("cleanroom", ignore_case = TRUE)) ~ "Respirator"),
    face_mask = case_when(
      str_detect(desc, fixed("medical", ignore_case = TRUE)) |
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) |
        str_detect(desc, fixed("dust mask", ignore_case = TRUE)) |
        str_detect(desc, fixed("ISO", ignore_case = FALSE)) |
        str_detect(desc, fixed("ASTM", ignore_case = FALSE))|
        str_detect(desc, fixed("ANSI", ignore_case = FALSE)) |
        str_detect(desc, fixed("AAMI", ignore_case = FALSE)) |
        str_detect(desc, fixed("level ", ignore_case = TRUE)) |
        str_detect(desc, "PPE") |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) |
        str_detect(desc, fixed("3M", ignore_case = FALSE)) |
        str_detect(desc, fixed("3-ply", ignore_case = FALSE)) |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) ~ "Face Mask")
  )
           
```

We use the following quality checks:

```{r, eval = FALSE}
thomas_struc %>% 
  filter(is.na(resp), is.na(face_mask)) %>% 
  view()
```

```{r, eval = FALSE}
thomas_struc %>% 
  filter(search_prod == "Face Masks", is.na(face_mask), !is.na(resp)) %>% 
  view()
```


```{r, eval = FALSE}
thomas_struc %>% 
  filter(search_prod == "Respirators", !is.na(face_mask), is.na(resp)) %>% 
  view()
```

We see that there are some entries that supply face masks that are not registered as haveing provided face masks. We cannot add "face mask" to our defintion of face mask because that would include some cloth masks that do not meet our standards. Thus, we perform the following correction: 

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(face_mask = case_when(
    (str_detect(desc, fixed("face mask", ignore_case = TRUE)) | str_detect(desc, fixed("disposable", ignore_case = TRUE)))
                  & !is.na(resp) & is.na(face_mask) ~ "Face Mask", 
    TRUE ~ face_mask 
  ))
```


```{r}
search_match <- thomas_struc %>% 
  group_by(search_prod) %>% 
  count(resp, face_mask)

search_match
```

After performing another set of quality checks to make sure our filters are effective, we are reasonably confident that these definitions segment our data appropriately.

We can now define a category of cloth mask (that is separate from either respirators or face masks). 

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(cloth_mask = case_when(
    (str_detect(desc, fixed("masks", ignore_case = TRUE))|
       str_detect(desc, fixed("face mask", ignore_case = TRUE)) | str_detect(desc, fixed("cloth mask", ignore_case = TRUE)) |
       str_detect(desc, fixed("sewn", ignore_case = TRUE)))
       & is.na(resp) & is.na(face_mask) ~ "Cloth Mask"))
```

```{r}
thomas_struc %>% 
  filter(cloth_mask == "Cloth Mask") %>% 
  count()
```

We can now create a specific product variable based on these new divisions. 

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(specific_product = case_when( 
    resp == "Respirator" & is.na(face_mask) ~ "Respirators Only", 
    face_mask == "Face Mask" & is.na(resp) ~ "Face Masks Only", 
    resp == "Respirator" & face_mask == "Face Mask" ~ "Respirators and Face Masks", 
    cloth_mask == "Cloth Mask" ~ "Cloth Masks"))
```

The last thing we will do is add a flag for if the company mentions that they are responding to COVID-19. 

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(covid_desc = str_detect(desc, fixed("covid", ignore_case = TRUE)) | str_detect(desc, fixed("coronavirus", ignore_case = TRUE)))
```

One thing we are intersted in is the overlap between companies registered in Thomasnet as responding to COVID-19 and companies that state covid-19 but are not registered. 

```{r}
thomas_struc %>% 
  filter(covid_19 == "COVID-19 Response") %>% 
  group_by(covid_19, specific_product) %>% 
  count(covid_desc)
```

```{r}
thomas_struc %>% 
  filter(is.na(covid_19)) %>% 
  group_by(specific_product) %>% 
  count(covid_desc)
```

We will need to determine which categories should toggle as "part of the COVID-19 response."

## Meets FDA or Technical Specs? 

The last thing that we do is specify if our product meets FDA or other technical specs.  

We define three categories: 

1. Affirmatively meets FDA needs/technical specs
2. Potentiall meets FDA needs/technical specs
3. NA

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(useful = case_when(
        str_detect(desc, fixed("N95", ignore_case = TRUE)) | 
      str_detect(desc, fixed("cleanroom", ignore_case = TRUE))|
        str_detect(desc, fixed("ISO", ignore_case = FALSE)) |
        str_detect(desc, fixed("ASTM", ignore_case = FALSE))|
        str_detect(desc, fixed("ANSI", ignore_case = FALSE)) |
        str_detect(desc, fixed("AAMI", ignore_case = FALSE)) |
        str_detect(desc, "FDA") |
        str_detect(desc, "NIOSH") |
        str_detect(desc, "801") |
        str_detect(desc, "KN95") |
        str_detect(desc, fixed("3M", ignore_case = FALSE)) |
        str_detect(desc, fixed("3-ply", ignore_case = FALSE)) ~ "Affirmatively",
      str_detect(desc, fixed("medical", ignore_case = TRUE)) |
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) |
        str_detect(desc, fixed("dust mask", ignore_case = TRUE)) |
        str_detect(desc, fixed("level ", ignore_case = TRUE)) |
        str_detect(desc, "PPE") |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) ~ "Possibly")
  )
        
```


```{r}
thomas_struc %>% 
  filter(useful == "Affirmatively") %>%
  group_by(specific_product) %>% 
  count() %>% 
  ggplot(aes(specific_product, n, fill = specific_product, label = n)) +
  geom_col() + 
  geom_label(show.legend = FALSE) +
  theme_bw() + 
  labs(title = "Number of Suppliers by Specific End Product Type", subtitle = "Affirmatively meet FDA Specs, Thomasnet 5/29/20", y = "", x = "", fill = "Specific Product") + 
  theme(axis.ticks.x = element_blank(), axis.text.x = element_blank())
```


## Analyzing Supplier Types 

We now turn to an anlysis of supplier types. Our goal is to differentiate between the different supplier types. 


```{r}
thomas_struc %>% 
  group_by(loc_desc) %>% 
  count() 
```

I propose the following breakdown: 

* Primary Manufacturer (primary purpose is manufacturer)
* Secondary Manufacturer (manufacturer not primary purpose, but is a purpose)
* Distributor (distributor as primary or secondary purpose, no manufacturing) 
* Other (not a distributor or a manufacturer)

```{r}
thomas_struc <- thomas_struc %>% 
  mutate(broad_loc = case_when(
    str_detect(loc_desc, "Manufacturer\\*") ~ "Primary Manufacturer", 
    str_detect(loc_desc, "Manufacturer") & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) ~ "Secondary Manufacturer",
    str_detect(loc_desc, "Distributor") | str_detect(loc_desc, "Manufacturers' Rep*") ~ "Distributor", 
    str_detect(loc_desc, "Manufacturer", negate = TRUE) & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) & 
      str_detect(loc_desc, "Distributor", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep*", negate = TRUE) ~ "Other"))
```

```{r}
thomas_struc %>% 
  group_by(broad_loc) %>% 
  count()
```

## Analyzing Capacity and Lead Time Data: 

The key question we try and answer here is: what do we have available? 

We now turn to an analysis of what information about capacity and lead time we can extract from our dataset. 

```{r}
capacity <- thomas_struc %>% 
  filter(str_detect(desc, fixed("capabilities", ignore_case = TRUE)) | 
           str_detect(desc, fixed("production", ignore_case = TRUE)) |
           str_detect(desc, fixed("per week", ignore_case = TRUE)) |
           str_detect(desc, fixed("per month", ignore_case = TRUE)) |
           str_detect(desc, fixed("million", ignore_case = TRUE)) |
           str_detect(desc, ",000") ) %>% 
  mutate(cap_info = 1)
```

There are 106 potential companies that we can extract some sort of actual production level information from. 

```{r}
lead_times <- thomas_struc %>% 
  filter(str_detect(desc, fixed("lead", ignore_case = TRUE)) |
           str_detect(desc, fixed("delivery", ignore_case = TRUE)) |
           str_detect(desc, fixed("delay", ignore_case = TRUE)) |
           str_detect(desc, fixed("lag", ignore_case = TRUE)) |
           str_detect(desc, fixed("ship", ignore_case = TRUE)) |
           
           str_detect(desc, fixed("weeks", ignore_case = TRUE))) %>% 
  mutate(lead_info = 1)
```

There are 149 observations with lead_times available. What is the overlap between our three categories? 

```{r}
thomas_info <- bind_rows(lead_times, capacity) 

cap_lead <- thomas_info %>% 
  group_by(company, location, loc_desc, broad_loc, desc, specific_product) %>% 
  count()
```

```{r}
cap_lead %>% 
  group_by(n) %>% 
  count()
```

There are 218 observations that we have potential information for either capacity or lead time, and 37 observations that we have potential information on both of them for. 

Our next step will be to determine exactly what information we can extract from this smaller dataset. We do this manually in excel. 

```{r, eval = FALSE}
write_csv(cap_lead, here("Data/cap_lead.csv"))
```


```{r, include = FALSE}
cap_lead_impute <- read_csv(here("Data/cap_lead_impute.csv"))
```

```{r}
cap_info <- cap_lead_impute %>% 
  filter(!is.na(product_capacity))
```


```{r}
cap_info %>% 
  group_by(specific_product) %>% 
  count()
```

```{r}
cap_info %>% 
  group_by(broad_loc) %>% 
  count()
```

```{r}
stock_info <- cap_lead_impute %>% 
  filter(!is.na(stock))
```

```{r}
stock_info %>% 
  group_by(broad_loc) %>% 
  count()
```

```{r}
lead_info <- cap_lead_impute %>% 
  filter(!is.na(lead_time)) 
```

```{r}
lead_info %>% 
  group_by(lead_time) %>% 
  count() %>% 
  filter(n > 3) %>% 
  ggplot(aes(lead_time, n))+
  geom_col() + 
  labs(title = "Most Frequent Lead Times", x = "", y = "") + 
  theme_bw()
```


```{r}
lead_info %>% 
  group_by(lead_time, broad_loc) %>% 
  filter(broad_loc %in% c("Distributor", "Primary Manufacturer")) %>% 
  count() %>% 
  filter(n > 1) %>% 
  ggplot(aes(lead_time, n))+
  geom_col()+
  coord_flip()+
  facet_wrap(~broad_loc) + 
  labs(title = "Comparisson of Lead Time Data", subtitle = "for Distributors and Primary Manufacturers", y = "", x = "") + 
  theme_bw()
```

```{r}
prod_lead <- lead_info %>% 
  filter(!is.na(specific_product)) %>% 
  group_by(lead_time, specific_product) %>% 
  count() %>% 
  filter(n > 1) %>% 
  ggplot(aes(lead_time, n))+
  geom_col()+
  coord_flip()+
  facet_wrap(~specific_product) + 
  labs(title = "Comparisson of Lead Time Data", subtitle = "by Specific Product", y = "", x = "") + 
  theme_bw()
```


```{r}
cap_lead <- cap_lead_impute %>% 
  select(c("company", "desc", product_capacity, lead_time, stock))
```

We now want to merge this back with our original dataset. 

```{r}
thomas_an <- left_join(thomas_struc, cap_lead)
```


```{r}
saveRDS(thomas_an, here("Data/fm_resp.RDS"))
```


