---
title: "thomasnet_cleaning_functions"
author: "Nikhil Kalathil"
date: "6/18/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include == FALSE }
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(ggthemes)
library(tm)
library(here)
library(lubridate)
```
# End products

## Defining Functions 

We now define a series of functions to clean weekly Thomasnet pulls. 

First, we define our directory: 

```{r}
dir <- "C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/Weekly Thomasnet Pulls"
```

Next, we define our functions. 

### Read Data and Bind Respirators and Face Masks Together

```{r}
desc_clean1 <- function(data){
  desc_dup <- data %>% 
    group_by(company, location, loc_desc) %>% 
    mutate(count = n())  %>% 
    filter(count >= 2) %>%
    ungroup() %>% 
    group_by(company) %>% 
    arrange(company)
  
   if(nrow(desc_dup) > 0){
     desc_dup <- desc_dup %>% 
       mutate(desc2 = lead(desc), 
              tal = seq(n()), 
              desc = paste(desc, desc2, sep = " DESCRIPTION 2: ")) %>% 
       filter(tal == 1) %>% 
       select(-c(tal, count, desc2))
   }

  
  desc1 <- anti_join(data, desc_dup, by = c("company", "location", "loc_desc"))
  
  desc_clean <- bind_rows(desc1, desc_dup) 
}
```




```{r}
read_bind <- function(date) {
  
  
  file_suffix <- paste(str_replace(date, "\\_", ""), "2020", sep = "")
  
  fm <- readRDS(paste("C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/Weekly Thomasnet Pulls/", date, "/thomas_fm_", file_suffix, ".RDS", sep ="")) %>% 
    desc_clean1()
  
  resp <- readRDS(paste("C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/Weekly Thomasnet Pulls/", date, "/thomas_resp_", file_suffix, ".RDS", sep ="")) %>% 
    desc_clean1()
  
    df <- bind_rows(resp, fm)
    
    return(df)
}
```

```{r}
test <- read_bind(date = '07_13')
```

### Remove Duplicates and Clean Words

```{r}
remove_dups <- function(data) {
  
  double <- data %>% 
  group_by(company, desc) %>% 
  mutate(n = n(), tal = seq(n())) %>% 
  filter(n == 2, tal == 1) %>% 
  mutate(search_product = "Face Masks and N95 Respirators") %>%
  select(-n)
  
  thomas_base <- anti_join(data, double, by = c("company", "desc")) %>% 
  bind_rows(double)
  
  thomas_clean1 <- thomas_base %>% 
  mutate(desc = str_replace(desc, fixed("covid 19", ignore_case = TRUE), "covid-19"), 
         desc = str_replace(desc, fixed("non woven", ignore_case = TRUE), "non-woven"), 
         desc = str_replace(desc, fixed("melt blown", ignore_case = TRUE), "melt-blown"),
         desc = str_replace(desc, fixed("meltblown", ignore_case = TRUE), "melt-blown"),
         desc = str_replace(desc, fixed("3 ply", ignore_case = TRUE), "3-ply"),
         desc = str_replace(desc, fixed("3ply", ignore_case = TRUE), "3-ply"),
         desc = str_replace(desc, fixed("clean room", ignore_case = TRUE), "cleanroom"),
         desc = str_replace(desc, fixed("spun bond", ignore_case = TRUE), "spunbond"),
         desc = str_replace(desc, fixed("spun-bond", ignore_case = TRUE), "spunbond")
         ) %>% 
  filter(str_length(desc) > 2)
  
  recat <- thomas_clean1 %>% 
    group_by(company, location, loc_desc) %>% 
    mutate(count = n())  %>% 
    filter(count >= 2, str_detect(location, "Multiple", negate = TRUE)) %>%
    ungroup() %>% 
    group_by(company) %>% 
    arrange(company) %>% 
    mutate(desc2 = lead(desc), 
         tal = seq(n()), 
         desc = paste(desc, desc2, sep = " DESCRIPTION 2: ")) %>% 
    filter(tal == 1) %>% 
    select(-c(tal, count, desc2))
  
  thomas_an <- anti_join(thomas_clean1, recat, by = c("company", "location", "loc_desc"))
  
  thomas_clean <- bind_rows(thomas_an, recat) %>% 
    mutate(broad_product = "End Product")
  
  return(thomas_clean)
    
}
```



```{r}
test_clean <- remove_dups(test)
```

### Define products and structure

```{r}
prod_struc1 <- function(data) {
  data %>% 
  mutate(resp = case_when(
    str_detect(desc, fixed("respirator", ignore_case = TRUE)) | 
      str_detect(desc, fixed("N95", ignore_case = TRUE)) | 
      (str_detect(desc, fixed("cleanroom", ignore_case = TRUE)) & (str_detect(desc, fixed("respirator", ignore_case = TRUE)) | str_detect(desc, fixed("mask", ignore_case = TRUE)))) ~ "Respirator"),
    face_mask = case_when(
      str_detect(desc, fixed("medical", ignore_case = TRUE)) |
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) |
        str_detect(desc, fixed("dust mask", ignore_case = TRUE)) |
        str_detect(desc, fixed("ISO", ignore_case = FALSE)) |
        str_detect(desc, fixed("ASTM", ignore_case = FALSE))|
        str_detect(desc, fixed("ANSI", ignore_case = FALSE)) |
        str_detect(desc, fixed("AAMI", ignore_case = FALSE)) |
        str_detect(desc, fixed("level ", ignore_case = TRUE)) |
        str_detect(desc, "PPE") |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) |
        str_detect(desc, fixed("3M", ignore_case = FALSE)) |
        str_detect(desc, fixed("3-ply", ignore_case = FALSE)) |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) ~ "Face Mask")
  ) 
    
}
```

```{r}
test_struc <- prod_struc1(test_clean)
```

```{r}
prod_struc2 <- function(data) {
  prod_struc1(data) %>% 
  mutate(face_mask = case_when(
    (str_detect(desc, fixed("face mask", ignore_case = TRUE)) | str_detect(desc, fixed("disposable", ignore_case = TRUE)))
                  & !is.na(resp) & is.na(face_mask) ~ "Face Mask", 
    TRUE ~ face_mask 
  ))
    
}
```

```{r}
test_struc <- prod_struc2(test_clean)
```

```{r}
prod_struc3 <- function(data) {
  prod_struc2(data) %>% 
  mutate(cloth_mask = case_when(
    (str_detect(desc, fixed("masks", ignore_case = TRUE))|
       str_detect(desc, fixed("face mask", ignore_case = TRUE)) | str_detect(desc, fixed("cloth mask", ignore_case = TRUE)) |
       str_detect(desc, fixed("sewn", ignore_case = TRUE)))
       & is.na(resp) & is.na(face_mask) ~ "Cloth Mask"))
}
```


```{r}
test_struc <- prod_struc3(test_clean)
```

```{r}
prod_struc <- function(data) { 
  prod_struc3(data) %>% 
    mutate(specific_product = case_when( 
    resp == "Respirator" & is.na(face_mask) ~ "Respirators Only", 
    face_mask == "Face Mask" & is.na(resp) ~ "Face Masks Only", 
    resp == "Respirator" & face_mask == "Face Mask" ~ "Respirators and Face Masks", 
    cloth_mask == "Cloth Mask" ~ "Cloth Masks"), 
    specific_product = if_else(      str_detect(company, "Chicago Embroidery Co."), "Cloth Masks", specific_product))
  }
```

```{r}
test_struc <- prod_struc(test_clean)
```


### Define Covid Participation 

```{r}
covid_part <- function(data){
  data %>% 
    mutate(covid_desc = str_detect(desc, fixed("covid", ignore_case = TRUE)) | str_detect(desc, fixed("coronavirus", ignore_case = TRUE)))
}
```

### Define Usefulness Categrogies

```{r}
fda_specs_old <- function(data) {
  data %>% 
    mutate(useful = case_when(
        str_detect(desc, fixed("N95", ignore_case = TRUE)) | 
      str_detect(desc, fixed("cleanroom", ignore_case = TRUE))|
        str_detect(desc, fixed("ISO", ignore_case = FALSE)) |
        str_detect(desc, fixed("ASTM", ignore_case = FALSE))|
        str_detect(desc, fixed("ANSI", ignore_case = FALSE)) |
        str_detect(desc, fixed("AAMI", ignore_case = FALSE)) |
        str_detect(desc, "FDA") |
        str_detect(desc, "NIOSH") |
        str_detect(desc, "801") |
        str_detect(desc, "KN95") |
        str_detect(desc, fixed("Brands+ 3M", ignore_case = FALSE)) |
        str_detect(desc, fixed("3-ply", ignore_case = FALSE)) ~ "Affirmatively",
      str_detect(desc, fixed("medical", ignore_case = TRUE)) |
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) |
        str_detect(desc, fixed("dust mask", ignore_case = TRUE)) |
        str_detect(desc, fixed("level ", ignore_case = TRUE)) |
        str_detect(desc, "PPE") |
        str_detect(desc, fixed("non-woven", ignore_case = FALSE)) ~ "Possibly")
  )
}
```

```{r}
fda_specs <- function(data) {
  data %>% 
    mutate(useful = case_when(
        str_detect(desc, fixed("N95", ignore_case = TRUE)) | 
        str_detect(desc, fixed("ASTM", ignore_case = FALSE))|
        str_detect(desc, fixed("ANSI", ignore_case = FALSE)) |
        str_detect(desc, fixed("AAMI", ignore_case = FALSE)) |
        str_detect(desc, "FDA") |
        str_detect(desc, "NIOSH") |
        str_detect(desc, "801") |
        str_detect(desc, "KN95") |
        str_detect(desc, fixed("Brands+ 3M", ignore_case = FALSE))  ~ "Affirmatively",
        str_detect(desc, fixed("3-ply", ignore_case = TRUE)) | 
        (str_detect(desc, fixed("cleanroom", ignore_case = TRUE)) & (str_detect(desc, fixed("respirator", ignore_case = TRUE)) | str_detect(desc, fixed("mask", ignore_case = TRUE)))) |
        str_detect(desc, fixed("ISO", ignore_case = FALSE)) |
        str_detect(desc, fixed("medical", ignore_case = TRUE)) |
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) |
        str_detect(desc, fixed("dust mask", ignore_case = TRUE)) |
        str_detect(desc, fixed("level ", ignore_case = TRUE)) |
        str_detect(desc, "PPE") | 
        str_detect(desc, fixed("non-woven", ignore_case = TRUE)) ~ "Possibly")
  )
}
```

### Define Medical Market

```{r}
med_mark <- function(data) { 
  data %>% 
    mutate(medical_market = case_when(
      str_detect(desc, fixed("hospital", ignore_case = TRUE)) |
        str_detect(desc, fixed("medical", ignore_case = TRUE)) | 
        str_detect(desc, fixed("surgical", ignore_case = TRUE)) |
        str_detect(desc, fixed("dental", ignore_case = TRUE)) |
        str_detect(desc, fixed("PPE", ignore_case = FALSE)) |
        str_detect(desc, fixed("veterinary", ignore_case = TRUE)) ~ "Serving Medical Market"
    )) %>% 
    mutate(medical_market = case_when(
      is.na(medical_market) ~ "Unknown", 
      TRUE ~ medical_market
    ))} 
```



### Define Suppliers

```{r}
suppliers <- function(data){ 
  data %>% 
    mutate(broad_loc = case_when(
    str_detect(loc_desc, "Manufacturer\\*") ~ "Primary Manufacturer", 
    str_detect(loc_desc, "Manufacturer") & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) ~ "Secondary Manufacturer",
    str_detect(loc_desc, "Distributor") | str_detect(loc_desc, "Manufacturers' Rep*") ~ "Distributor", 
    str_detect(loc_desc, "Manufacturer", negate = TRUE) & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) & 
      str_detect(loc_desc, "Distributor", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep*", negate = TRUE) ~ "Other"))
  }
```


### Stitch all functions together

```{r}
clean_endprods <- function(date){
  
  raw <- read_bind(date)
  
  file_suffix <- paste(str_replace(date, "\\_", ""), "2020", sep = "")
  
  raw %>% 
    remove_dups() %>% 
    prod_struc() %>% 
    covid_part() %>% 
    fda_specs() %>% 
    suppliers() %>%
    med_mark() %>% 
      mutate(date = mdy(file_suffix))
    
    
}
```

```{r}
thomas_test <- clean_endprods("06_05")
```


## Combining datasets

```{r}
thomas_files <- list()

file_list <- list.files(dir)

i <- 1

for (file in 1:length(file_list)) {
  
  filename <- file_list[file]
  
  print(filename)
  
  thomas_files[[file]] <- clean_endprods(filename)
  
  i <- i+1
}
```

```{r}
thomas_endprods <- bind_rows(thomas_files[[1]], thomas_files[[2]]) %>% 
  bind_rows(thomas_files[[3]]) %>% 
  bind_rows(thomas_files[[4]]) %>% 
  bind_rows(thomas_files[[5]]) %>% 
  bind_rows(thomas_files[[6]]) %>% 
  bind_rows(thomas_files[[7]]) %>% 
  bind_rows(thomas_files[[8]])
```

```{r}
dir1 <- "C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/thomasnet_totals"
saveRDS(thomas_endprods, paste(dir1, "/thomas_endprods.RDS", sep = ""))
```

# Intermediary Products

## Defining Functions

We define our functions for our intermediary data

### Read Data

```{r}
read_nw <- function(date) {
  
  file_suffix <- paste(str_replace(date, "\\_", ""), "2020", sep = "")

  
  df <- readRDS(paste("C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/Weekly Thomasnet Pulls/", date, "/nonwoven_", file_suffix, ".RDS", sep ="")) %>% 
    desc_clean1()
  
    
    return(df)
}
```

```{r}
read_lat <- function(date) {
  
  file_suffix <- paste(str_replace(date, "\\_", ""), "2020", sep = "")

  df <- readRDS(paste("C:/Users/surface/Box/COVID 19 Master Folder/Data/Masks/Weekly Thomasnet Pulls/", date, "/nolatex_", file_suffix, ".RDS", sep =""))
  
    
    return(df)
}

```


### Affirmatively Producing Covid-19 Relevant Fabric

```{r}
cat_1 <- function(data) {
  data %>% 
    mutate(desc = str_replace(desc, fixed("spun bond", ignore_case = TRUE), "spunbond"), 
           desc = str_replace(desc, fixed("spun-bond", ignore_case = TRUE), "spunbond"), 
           desc = str_replace(desc, fixed("melt blown", ignore_case = TRUE), "meltblown"),
           desc = str_replace(desc, fixed("melt-blown", ignore_case = TRUE), "meltblown"), 
           desc = str_replace(desc, fixed("needlepunch", ignore_case = TRUE), "needle punch")) %>% 
    mutate(cat_1 = case_when(
        str_detect(desc, fixed("spunbond", ignore_case = TRUE)) | 
        str_detect(desc, fixed("meltblown", ignore_case = TRUE)) ~ "cat_1"))
}
  
```

### Produces a product that is potentially useable for COVID-19 masks and respirators. 

```{r}
cat_2 <- function(data) {
  data %>% 
    cat_1() %>% 
    mutate(cat_2 = case_when(
      (str_detect(desc, fixed("spunlace", ignore_case = TRUE)) |
      str_detect(desc, fixed("hydroentangled", ignore_case = TRUE)) |
      str_detect(desc, fixed("ghz", ignore_case = TRUE)) |
      str_detect(desc, fixed("gsm", ignore_case = TRUE)) |
      str_detect(desc, fixed("electrospun", ignore_case = TRUE)) | 
      str_detect(desc, "silver") | 
      str_detect(desc, "nickel"))  ~ "cat_2")) %>% 
    mutate(cat_2 = case_when(
      cat_1 == "cat_1" ~ NA_character_,
      TRUE ~ cat_2
    ))
}
```

### Category 3 and Coatings

Category 3 mention none of the other categories, but do mention coatings. We remove mentions of vinyl coatings as these tend to relate to furniture. 

```{r}
cat_3 <- function(data) {
  data %>% 
    cat_1() %>% 
    cat_2() %>% 
    mutate(cat_3 = case_when(
      str_detect(desc, "ISO") |
      str_detect(desc, fixed("needle punch", ignore_case = TRUE)) | 
      str_detect(desc, fixed("polypropylene", ignore_case = TRUE)) ~ "cat_3")) %>% 
    mutate(cat_3 = case_when(
      cat_1 == "cat_1" | cat_2 == "cat_2" ~ NA_character_,
      TRUE ~ cat_3
    ))
    
}
```

### Filter Out Unrelated Entries and Define Our Toggle 

We now filter out entries that fit none of the above categories.

```{r}
fda_specs_nw <- function(data) {
  data %>%
    cat_3() %>% 
    med_mark() %>% 
    filter(!is.na(cat_1) | !is.na(cat_2) | !is.na(cat_3) | medical_market != "Unknown") %>% 
  mutate(useful = case_when(
    cat_1 == "cat_1" ~ "Affirmatively", 
    cat_2 == "cat_2" ~ "Possibly",
    cat_3 == "cat_3" ~ "Unknown"
  ))
}
```

```{r}
fda_specs_lat <- function(data) {
  data %>% 
  mutate(useful = "Affirmatively")
}
```

### Suppliers and Stiching Functions

```{r}
clean_int <- function(date) {
  
  file_suffix <- paste(str_replace(date, "\\_", ""), "2020", sep = "")
  
  nw <- read_nw(date) %>% 
    fda_specs_nw()
  lat <- read_lat(date) %>% 
    fda_specs_lat()
  
  int_comb <- bind_rows(nw, lat) %>% 
    med_mark()
  
  int_comb %>% 
  mutate(broad_loc = case_when(
    str_detect(loc_desc, "Manufacturer\\*") ~ "Primary Manufacturer", 
    str_detect(loc_desc, "Manufacturer") & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) ~ "Secondary Manufacturer",
    str_detect(loc_desc, "Distributor") | str_detect(loc_desc, "Manufacturers' Rep*") ~ "Distributor", 
    str_detect(loc_desc, "Manufacturer", negate = TRUE) & str_detect(loc_desc, "Manufacturer\\*", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep", negate = TRUE) & 
      str_detect(loc_desc, "Distributor", negate = TRUE) &
      str_detect(loc_desc, "Manufacturers' Rep*", negate = TRUE) ~ "Other")) %>% 
    mutate(date = mdy(file_suffix))
    
  
}
```

## Combining All Data


```{r}
thomas_files <- list()

file_list <- list.files(dir)

i <- 1

for (file in 1:length(file_list)) {
  
  filename <- file_list[file]
  
  print(filename)
  
  thomas_files[[file]] <- clean_int(filename)
  
  i <- i+1
}
```

```{r}
thomas_intprods <- bind_rows(thomas_files[[1]], thomas_files[[2]]) %>% 
  bind_rows(thomas_files[[3]]) %>% 
  bind_rows(thomas_files[[4]]) %>% 
  bind_rows(thomas_files[[5]]) %>% 
  bind_rows(thomas_files[[6]]) %>% 
  bind_rows(thomas_files[[7]]) %>% 
  bind_rows(thomas_files[[8]])
```

```{r}
saveRDS(thomas_intprods, paste(dir1, "/thomas_intprods.RDS", sep = ""))
```

```{r}
thomas_prods <- bind_rows(thomas_endprods, thomas_intprods)
```

```{r}
saveRDS(thomas_prods, paste(dir1, "/thomas_allprods.RDS", sep = ""))
```

```{r}
saveRDS(thomas_prods, here("Data/Cleaned/thomas_allprods.RDS"))
```

```{r}
saveRDS(thomas_intprods, here("Data/Cleaned/int_prod.RDS"))
```

```{r}
saveRDS(thomas_endprods, here("Data/Cleaned/fm_resp.RDS"))
```


