---
title: "Mapping and Analysis of Manually Cleaned Data"
author: "Nikhil Kalathil"
date: "08/01/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document takes manually checked data on domestic manufacturing locations, builds a geocoded company-location-address base sheet to reference all files against, creates a few summary graphs, and formats the data to be used in leaflet mapping. 

```{r, include == FALSE }
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(ggthemes)
library(tm)
library(here)
library(ggrepel)
library(lubridate)
library(ggnewscale)
library(readxl)
library(htmltools)
library(htmlwidgets)
library(RJSONIO)
```
```{r}

box_dir <- "C:/Users/Nikhil Kalathil/Box/COVID 19 Master Folder/Data/Masks/"

```

```{r}
box_here <- function(file) {
  paste(box_dir, file, sep = "")
}
```



```{r}
thomas_an <- readRDS(here("Data/Cleaned/fm_resp.RDS"))
int_prod <- readRDS(here("Data/Cleaned/int_prod.RDS"))
```

```{r}
int_prod <- int_prod %>% 
  mutate(company = if_else(company == "Precision Custom Coatings LLC", "Precision Textiles", company))
```


```{r}
thomas_struc <- bind_rows(int_prod, thomas_an) %>% 
  mutate(broad_loc = case_when(
    str_detect(broad_loc, "Manuf") ~ "Manufacturer", 
    str_detect(broad_loc, "Dist") ~ "Distributor",
    TRUE ~ "Other/Unknown"
  ), 
  broad_loc = case_when(
    str_detect(desc, fixed("distributor", ignore_case = TRUE)) & str_detect(desc, fixed("manufacturer", ignore_case = TRUE), negate = TRUE) ~ "Distributor", 
    TRUE ~ broad_loc
  )) %>%  
  mutate(useful == if_else(company %in% c("Prestige Ameritech", "Huajian US Services, Corp", "Bossong Hosiery Mills, Inc."), "Affirmatively", useful)) %>% 
  group_by(specific_product, company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

## Differentiating by Supplier Type
```{r}
my_pal <- c(brewer.pal(4, "Set3")[4], brewer.pal(4, "Paired")[2])
```


```{r}
sup1 <- thomas_struc %>% 
  group_by(date, broad_product, specific_product, broad_loc) %>% 
  filter(specific_product != "NA") %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  ),
  pos_loc = case_when(
    broad_loc == "Manufacturer" ~ 1, 
    broad_loc == "Distributor" ~ 2, 
    broad_loc == "Other/Unknown" ~ 3
  )) %>% 
  filter(broad_loc != "Other/Unknown") %>% 
  mutate(specific_product = reorder(specific_product, pos), 
         broad_loc = reorder(broad_loc, -pos_loc)) %>% 
  ggplot(aes(date, n, fill = broad_loc, group = broad_loc)) +
  geom_area(position = "stack", show.legend = FALSE, color = "Black", alpha = 0.8 ) +
  geom_point(shape =21, color = "Black", alpha = 0.7, size = 1 ,position = "stack") +
  scale_fill_manual(values = my_pal) + 
  facet_wrap(~reorder(specific_product, pos)) +
  labs(title = "Number of Suppliers by Product and Thomasnet Supplier Type", subtitle = "Thomasnet 05/30/20 - 11/02/20", y = "Unique Thomasnet Suppliers", x = "", fill = "Supplier Type") + 
  theme_bw()

sup1
```

# Base Graphs

```{r}
thomas_graph <- thomas_struc %>%  
  filter(specific_product != "NA", broad_loc == "Manufacturer" ) %>% 
  mutate(useful = case_when(
    is.na(useful) ~ "Unknown", 
    TRUE ~ useful
  )) %>% 
  mutate(useful = if_else(medical_market == "Serving Medical Market" & useful != "Affirmatively", "Possibly", useful)) %>% 
  group_by(date, broad_product, specific_product, useful) %>% 
  count()  %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos)) %>% 
  pivot_wider(c(date, specific_product, pos), names_from = useful, values_from = n, values_fill = 0) %>% 
  mutate(Affirmatively= case_when(
    specific_product == "Respirators and Face Masks" ~ Affirmatively - 1, 
    TRUE ~ as.double(Affirmatively)),
    n_all = Affirmatively + Possibly + Unknown, 
    n_poss_aff = Affirmatively + Possibly)
```

```{r}
slice_date <- mdy("11/17/2020")
```

```{r}
thomas_graph_slice <- thomas_graph %>% 
  filter(date == slice_date)
```

```{r}
med_count <- function(data){
  data %>% 
    filter(specific_product != "NA", broad_loc == "Manufacturer", broad_product == "Intermediary Product") %>% 
    filter(medical_market != "Unknown") %>% 
    mutate(useful = case_when(
      is.na(useful) ~ "Unknown", 
      TRUE ~ useful
    )) %>% 
    group_by(date, broad_product, specific_product, useful) %>% 
    count() %>% 
    ungroup() %>% 
    mutate(pos = case_when(
      specific_product == "Respirators and Face Masks" ~ 1, 
      specific_product == "Face Masks Only" ~ 2, 
      specific_product == "Respirators Only" ~ 3, 
      specific_product == "Non-Woven Fabric" ~ 5, 
      specific_product == "No Latex Elastic" ~ 6,
      specific_product == "Cloth Masks" ~ 4, 
    )) %>% 
    mutate(specific_product = fct_reorder(specific_product, -pos),
           n_aff = case_when(
             useful == "Affirmatively" ~ n
           ),
           n_poss = case_when(
             useful %in% c("Possibly") ~ n
           ))
}
```
```{r}
med_graph_slice <- thomas_struc  %>% 
  med_count() %>%  
  filter(date == slice_date)
```


```{r}
test_c <- c(brewer.pal(6, "Set2")[6], brewer.pal(6, "Set2")[5], brewer.pal(6, "Set2")[4], brewer.pal(6, "Set2")[3], brewer.pal(6, "Set2")[2], brewer.pal(6, "Set2")[1])
```


```{r}
my_pal2 <- c("#E6BB00", "#75a626")
```



```{r}
fig_1 <- thomas_graph_slice %>% 
  ggplot() + 
  scale_fill_manual(values = test_c) + 
  geom_col(aes(specific_product, n_all, fill = specific_product), alpha = 0.3, position = "stack", show.legend = FALSE)  +
  geom_col(data = thomas_graph_slice, aes(specific_product, n_poss_aff, fill = specific_product), alpha = 0.7, color = "dark grey", position = "stack", show.legend = FALSE)  +
    geom_col(data = thomas_graph_slice, aes(specific_product, Affirmatively, fill = specific_product), alpha = 0.9, color = "black", position = "stack", show.legend = FALSE) +
  geom_label(data = thomas_graph_slice, aes(specific_product, Affirmatively, fill = specific_product, label = Affirmatively), show.legend = FALSE) +
  new_scale_fill() + 
  geom_col(data = med_graph_slice, aes(specific_product, n_aff, fill = specific_product), show.legend = FALSE) + 
  scale_fill_manual(values = my_pal2) + 
  geom_text(data = med_graph_slice, aes(specific_product, n_aff, label = n_aff), hjust = 1 ) + 
  labs(title = "Number of Potential Domestic Manufacturing Entities by Product Type", subtitle = "Source: Thomasnet, 11/17/20. Manufacturers Self-Identifying as: \nProducing Standard Products for FDA Approved, Hospital Grade Masks/Respirators", x = "", y = "Unique Manufacturing Entities") + 
  coord_flip() +
  theme_bw()

fig_1
```

```{r}
fig_time <- thomas_graph %>% 
  ggplot() +
    geom_area(aes(date, n_all, fill = specific_product), alpha = 0.3, position = "stack", show.legend = FALSE) +
  scale_fill_manual(values = test_c) + 
  geom_point(aes(date, n_all, fill = specific_product), shape = 21, alpha = 0.3, color = "Black", show.legend = FALSE) +
  geom_area(aes(date, n_poss_aff, fill = specific_product), alpha = 0.7, color = "dark grey", position = "stack", show.legend = FALSE)  +
  geom_point(aes(date, n_poss_aff, fill = specific_product), shape = 21, alpha = 0.7, color = "Black", show.legend = FALSE) +
    geom_area(aes(date, Affirmatively, fill = specific_product), alpha = 0.9, color = "black", position = "stack", show.legend = FALSE) +
    geom_point(aes(date, Affirmatively, fill = specific_product), shape = 21, alpha = 0.9, color = "Black", show.legend = FALSE) +
  new_scale_fill() + 
  geom_area(data = med_graph, aes(date, n_aff, fill = specific_product), show.legend = FALSE) +
  geom_point(data = med_graph, aes(date, n_aff, fill = specific_product), shape = 21, color = "Black", show.legend = FALSE) +
  scale_fill_manual(values = my_pal2) + 
  labs(title = "Number of Potential Domestic Manufacturers by Product Type", subtitle = "Source: Thomasnet, 05/30/20 - 11/17/20. Domestic Manufacturers Self-Identifying as: \n1) Producing Standard Products for FDA Approved, Hospital Grade Masks; \n2) Producing Products that Meet Technical Requirements for Hospital Grade Masks; or \n3) Supplying the Medical Market", x = "", y = "") +
  facet_wrap(~reorder(specific_product, pos)) +
  theme_bw()

fig_time
```


# Importing Manually Checked Data

We begin with importing manually checked data for each product category. 

```{r}
aff_comps <- thomas_struc %>% 
  filter(specific_product != "NA", broad_loc == "Manufacturer" ) %>% 
  mutate(useful = case_when(
    is.na(useful) ~ "Unknown", 
    TRUE ~ useful
  )) %>%
  filter(useful == "Affirmatively") %>% 
  mutate(company = if_else(company == "Monadnock Paper Mills, Inc.", "Monadnock Non-Wovens LLC", company),
         company = if_else(company == "Consolidated Cordage Corporation", "Consolidated Cordage Corp.", company)) 
```

## Importing Data 

```{r}
conf_nl <- read_xlsx(box_here("manf_comps.xlsx"), sheet = "No Latex") %>% 
    filter(useful == "Affirmatively" | is.na(useful)) %>% 
  select(-(5:17)) %>% 
  mutate(from = 1, 
         specific_product = "No Latex Elastic",
         dom_useful = as.character(dom_useful))
```


```{r}
conf_nw <- read_xlsx(box_here("manf_comps.xlsx"), sheet = "Non Woven") %>% 
  filter(useful == "Affirmatively" | is.na(useful)) %>% 
  select(-(5:17)) %>% 
  mutate(from = 1, 
         specific_product = "Non-Woven Fabric")
```

```{r}
conf_resp <- read_xlsx(box_here("manf_comps.xlsx"), sheet = "Respirator Only") %>% 
  filter(useful == "Affirmatively" | is.na(useful)) %>% 
  select(-(5:17)) %>% 
  mutate(from = 1, 
         specific_product = "Respirators Only") 
```

```{r}
conf_fm <- read_xlsx(box_here("manf_comps.xlsx"), sheet = "FM Only") %>% 
  filter(useful == "Affirmatively" | is.na(useful)) %>% 
  select(-(6:17)) %>% 
  mutate(from = 1, 
         specific_product = "Face Masks Only") 
```

```{r}
conf_fmresp <- read_xlsx(box_here("manf_comps.xlsx"), sheet = "Resp & FM") %>% 
  filter(useful == "Affirmatively" | is.na(useful)) %>% 
  select(-(6:18)) %>% 
  mutate(from = 1, 
         specific_product = "Respirators and Face Masks") 
```

### Check for Each Product and Write New Entries to a CSV

#### NL Tests
```{r}
aff_nl <- aff_comps %>% 
  filter(specific_product == "No Latex Elastic") %>% 
  left_join(conf_nl)
```
```{r}
aff_nl %>% 
  view()
```

```{r}
aff_nl %>% 
  group_by(specific_product, date) %>% 
  count()
```

#### NW Tests
```{r}
aff_nw <- aff_comps %>% 
  filter(specific_product == "Non-Woven Fabric") %>% 
  left_join(conf_nw)
```

```{r}
aff_nw %>% 
  filter(is.na(from)) %>% 
  view()
```

```{r, eval = FALSE}
aff_nw %>% 
  filter(is.na(from)) %>% 
  write_csv(box_here("new_comps.csv"))
```

```{r}
aff_nw %>% 
  group_by(specific_product, date) %>% 
  count()
```

```{r}
aff_nw <- aff_nw %>% 
  group_by(company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```


#### Resp only tests
```{r}
aff_resp <- aff_comps %>% 
  filter(specific_product == "Respirators Only") %>% 
  left_join(conf_resp)
```
```{r}
aff_resp %>% 
  filter(is.na(from)) %>% 
  view()
```

```{r, eval = FALSE}
aff_resp %>% 
  filter(is.na(from)) %>% 
  write_csv(box_here("new_comps.csv"))
```


```{r}
aff_resp %>% 
  group_by(specific_product, date) %>% 
  count()
```



```{r}
aff_resp <- aff_resp %>% 
  group_by(company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

#### FM Only Tests
```{r}
aff_fm <- aff_comps %>% 
  filter(specific_product == "Face Masks Only") %>% 
  left_join(conf_fm)
```
```{r}
aff_fm %>% 
  filter(is.na(from)) %>% 
  view()
```

```{r}
aff_fm %>% 
  group_by(specific_product, date) %>% 
  count()
```

```{r, eval = FALSE}
aff_fm %>% 
  filter(is.na(from)) %>% 
  write_csv(box_here("new_comps.csv"))
```
```{r}
aff_fm <- aff_fm %>% 
  group_by(company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

#### FM+RESP Tests
```{r}
aff_fmresp <- aff_comps %>% 
  filter(specific_product == "Respirators and Face Masks") %>% 
  left_join(conf_fmresp) %>% 
    mutate(company = if_else(company == "RPB Safety", "RPB Safety, LLC.", company),
           company = if_else(company == "PZero Inc.", "PZero Innovations Inc.", company),
           company = if_else(company == "Pzero Innovations Inc.", "PZero Innovations Inc.", company),
           company = if_else(company == "Rhysley Ltd.", "Rhysley, Ltd.", company),
           company = if_else(company == "Y-Not Design & Mfg. Inc", "Y-Not Design & Mfg. Inc.", company), 
           company = if_else(company == "Lynktrac Technologies, LLC", "LynkTrac Technologies, LLC", company),
           company = if_else(company == "Cura, a Division of CustomFab USA", "Ceemly, a Division of CustomFab USA", company)) 
```

```{r}
aff_fmresp %>% 
  filter(is.na(from)) %>% 
  view()
```

```{r, eval = FALSE}
aff_fmresp %>% 
  filter(is.na(from)) %>%
  write_csv(box_here("new_comps.csv"))
```


```{r}
aff_fmresp %>% 
  group_by(specific_product, date) %>% 
  count()
```

```{r}
aff_fmresp <- aff_fmresp %>% 
  group_by(company, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```



### Combine and Graph 

```{r}
all_dom <- bind_rows(aff_nl, aff_nw) %>%
  bind_rows(aff_fm) %>% 
  bind_rows(aff_resp) %>% 
  bind_rows(aff_fmresp) %>% 
  mutate(specific_product = if_else(company %in% c("Safe Health", "Luosh USA, LLC", "PandMedic Solutions", "Alpha Pro Tech, Ltd.", "Guardis Medical
"), "Respirators and Face Masks", specific_product)) %>% 
  group_by(company, specific_product, date) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```
```{r}
all_dom %>% 
  group_by(specific_product, date) %>% 
  count()
```
```{r}
all_dom <- all_dom %>% 
  mutate(iso_only = str_detect(confirmation, "ISO")) %>%
  mutate(dom_useful = case_when(
    iso_only == 1 & str_detect(confirmation, "China", negate = TRUE) ~ "Possibly", 
    TRUE ~ dom_useful
  ))
```

For each product, for companies that list themselves as affirmatively producing a standard FDA product for surgical grade masks/respirators, we have manually checked every entry. We now list our confirmed companies and build our graphs for analysis. 

```{r}
conf_dom <- all_dom %>% 
  ungroup() %>% 
  filter(dom_useful == 1) %>% 
  select(company, address, facility_size_dbh, desc, specific_product, date, specific_product, sales, employees, date_founded, manf_loc, corporate_family_dbh, comp_type_dbh, all_site_emp_dbh, sales_dbh) %>%
  group_by(company) %>% 
  mutate(min_date = min(ymd(date)),
         max_date = max(ymd(date))) %>% 
    group_by(company, specific_product) %>%
  mutate(tot = n(), tal = seq(n())) %>% 
  filter(tal == 1)
```

```{r, eval = FALSE}
write_csv(conf_dom, box_here("confirmed_domestic.csv"))
```


## Zooming in


```{r}
dom_colors <- c(brewer.pal(6, "Set2")[1], brewer.pal(6, "Set2")[2], brewer.pal(6, "Set2")[3], brewer.pal(6, "Set2")[5], brewer.pal(6, "Set2")[6])
```


```{r}
aff_dom <- all_dom %>% 
  filter(dom_useful == 1) %>% 
  group_by(date, specific_product) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos)) #%>% 
  #mutate(n = case_when(
           #pos == 2 & date == ymd("2020-09-08") ~ 9,
           #pos == 2 & date != ymd("2020-09-08") ~ as.double(n), 
         #pos != 2 ~ as.double(n)))
```

```{r}
aff_dom_slice <- aff_dom %>% 
  filter(date == slice_date) %>% 
  mutate(n = case_when(
    specific_product == "Face Masks Only" ~ 14,
    specific_product == "Respirators Only" ~ 2,
    TRUE ~ as.double(n)
  ))
```

```{r}
neg_dom <- all_dom %>% 
  group_by(date, broad_product, specific_product) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos))
```

```{r}
neg_dom_slice <- neg_dom %>% 
  filter(date == slice_date)
```

```{r}
poss_dom <- all_dom %>% 
  filter(dom_useful == "Possibly" | dom_useful == "1") %>% 
  group_by(date, broad_product, specific_product) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, -pos))
```

```{r}
poss_dom_slice <- poss_dom %>% 
  filter(date == slice_date)  
```

```{r}
base_graph <- thomas_struc %>% 
    filter(broad_loc == "Manufacturer") %>% 
    filter(specific_product != "Cloth Masks", date == mdy("07/13/20")) %>% 
    group_by(broad_product, specific_product) %>% 
    filter(specific_product != "NA") %>% 
    count() %>% 
    mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
    ungroup() %>% 
    mutate(specific_product = reorder(specific_product, -pos) ) %>% 
  ggplot(aes(specific_product, n, fill = specific_product, label = n)) +
    scale_fill_manual(values = dom_colors) +
    theme_bw()
```


```{r}
label_data <- aff_dom_slice %>% 
  rename(aff_n = n) %>% 
  left_join(poss_dom_slice) %>% 
  rename(poss_aff_n = n) %>% 
  left_join(neg_dom_slice) %>% 
  mutate(neg_n = n - poss_aff_n)
```

```{r}
fig_2 <- base_graph + 
  coord_flip() +
  geom_col(data = neg_dom_slice, aes(specific_product, n, fill = reorder(specific_product, pos)), show.legend = FALSE, position = "stack", color = "Black") +
  geom_col(data = neg_dom_slice, aes(specific_product, n), position = "stack", show.legend = FALSE, fill = "Black", color = "Black") +
  geom_col(data = poss_dom_slice, aes(specific_product, n), position = "stack", show.legend = FALSE, fill = "Light Grey", color = "Black") +
  geom_label(data = label_data, aes(specific_product, poss_aff_n, label = neg_n), fill = "Black", color = "Light Grey", size = 3, position = "stack", hjust = 1) + 
  geom_col(data = aff_dom_slice, aes(reorder(specific_product, pos)), fill = "Light Blue", color = "Black") +
  geom_label(data = neg_dom_slice, aes(label = n, fill = reorder(specific_product, pos)), show.legend = FALSE, color = "Black") +
  geom_label(data = aff_dom_slice, aes(label = n), fill = "Light Blue", size = 3, color = "Black", show.legend = FALSE, y = 0) + 
  labs(x = "", y = "Unique Manufacturing Entities", title = "Confirmed Domestic Manufacturers (Blue), Unknown Manufacturing Entities (Grey), and \nConfirmed Non-Domestic or Non-manufacturing Entities (Black)", subtitle = "Source: Thomasnet, 11/17/20. Manufacturers Self-Identifying as: \nProducing Standard Products for FDA Approved, Hospital Grade Masks", fill = "Specific Product") 
```


```{r}
base2 <- all_dom %>% 
  group_by(date, broad_product, specific_product) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(pos = case_when(
    specific_product == "Respirators and Face Masks" ~ 1, 
    specific_product == "Face Masks Only" ~ 2, 
    specific_product == "Respirators Only" ~ 3, 
    specific_product == "Non-Woven Fabric" ~ 5, 
    specific_product == "No Latex Elastic" ~ 6,
    specific_product == "Cloth Masks" ~ 4, 
  )) %>% 
  mutate(specific_product = fct_reorder(specific_product, pos)) %>%
  filter(specific_product == "Respirators and Face Masks") %>% 
  ggplot(aes(date, n, fill = specific_product, group = specific_product)) +
  scale_fill_manual(values = dom_colors) + 
  facet_wrap(~reorder(specific_product, pos)) +
  theme_bw()
```

```{r}
time_conf <- base2 + 
  geom_area(data = neg_dom, aes(date, n, group = specific_product), position = "stack", fill = "Black", color = "White") +
  geom_area(data = poss_dom, aes(date, n, group = specific_product), position = "stack", fill = "Light Grey", color = "White") + 
  geom_area(data = aff_dom, aes(date, n, group = specific_product), position = "stack", fill = "Light Blue", color = "White") + 
  geom_point(shape = 21, size = 2, position = "stack", show.legend = FALSE, color = "Black") +
  geom_point(data = aff_dom, aes(date, n, group = specific_product), position = "stack", shape = 21, size = 2, fill = "Light Blue", color = "Black") +
  labs(title = "Confirmed Domestic Manufacturers (Blue), Unknown Manufacturing Entities (Grey), and \nConfirmed Non-Domestic or Non-manufacturing Entities (Black)", subtitle = "Thomasnet 05/30/20 - 11/17/20 \nManufacturers Self-Identifying as: \nProducing Standard Products for FDA Approved, Hospital Grade Masks/Respirators", y = "Unique Manufacturing Entities", x = "") 
```

# Geocoding


```{r, echo = FALSE, Include = FALSE}
api_key <- c("AIzaSyA1pwzK3BaX7_um-_TUrS7aGfCHQvp68b8")
```

We define our function, which will take an address as an input and output a latitude and longitude result. 

```{r}
geocodeAddress <- function(address) {
  require(RJSONIO)
  url <- "https://maps.googleapis.com/maps/api/geocode/json?address="
  url <- URLencode(paste(url, address, sep = ""))
  url <- URLencode(paste(url, "&key=", api_key, sep = ""))
  x <- fromJSON(url, simplify = FALSE)
  print(x$status)
  if (x$status == "OK") {
    out <- c(x$results[[1]]$geometry$location$lng,
             x$results[[1]]$geometry$location$lat,
             x$results[[1]]$formatted_address)
  } else {
    out <- NA
  }
  Sys.sleep(0.2)  # API only allows 5 requests per second
  out
}
```

```{r}
conf_fil <- function(data) {
  data %>% 
    filter(dom_useful == 1 | !is.na(DUNS)) %>% 
    filter(!dom_useful %in% c("0", "Possibly"))
}
``` 

```{r}
conf_fil(conf_fmresp) %>% 
  view()
```


```{r}
conf_all <- bind_rows(conf_nl, conf_nw) %>% 
  bind_rows(conf_resp) %>% 
  bind_rows(conf_fm) %>% 
  bind_rows(conf_fmresp)
```

```{r}
conf_all <-   conf_all %>% 
  mutate(iso_only = str_detect(confirmation, "ISO")) %>%
  mutate(dom_useful = case_when(
    iso_only == 1 & str_detect(confirmation, "China", negate = TRUE) ~ "Possibly", 
    TRUE ~ dom_useful
  )) %>% 
  conf_fil()
```

```{r}
conf_all_maps <- conf_all %>% 
   mutate(comp_address = paste(company, address, sep = ", ")) %>% 
  mutate(specific_product = if_else(company %in% c("Safe Health", "Luosh USA, LLC", "PandMedic Solutions", "Alpha Pro Tech, Ltd."), "Respirators and Face Masks", specific_product)) %>% 
  group_by(company, address) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal == 1)
```

```{r, include = FALSE}
for(i in 1:nrow(conf_all_maps))
{
  result <- geocodeAddress(conf_all_maps$address[i])
  conf_all_maps$long[i] <- as.numeric(result[1])
  conf_all_maps$lat[i] <- as.numeric(result[2])
  conf_all_maps$form_address[i] <- as.character(result[3])

}
```

```{r}
conf_all_maps %>% 
  filter(form_address == "United States" | is.na(form_address)) %>%
  select(company, address, form_address, specific_product) %>% 
  view()
```

```{r}
conf_all_maps <- conf_all_maps %>% 
  mutate(broad_product = case_when(
    specific_product %in% c("Respirators Only", "Respirators and Face Masks", "Face Masks Only") ~ "End Product", 
    specific_product %in% c("Non-Woven Fabric", "No Latex Elastic") ~ "Intermediary Product"
    ))
```


```{r}
conf_all_maps %>% 
  saveRDS(box_here("thomasnet_totals/conf_manfs_geocoded.RDS"))
```

```{r}
conf_all_maps <- readRDS(box_here("thomasnet_totals/conf_manfs_geocoded.RDS"))
```


```{r}
conf_all_maps <- conf_all_maps %>%
  ungroup() %>% 
  group_by(company, specific_product) %>% 
  mutate(hq= case_when(
    str_detect(comp_type_dbh, "HQ") | str_detect(comp_type_dbh, "Private Independent") | (is.na(comp_type_dbh) & manf_loc == 1 & max(seq(n())) ==1 ) ~ "HQ" , 
    str_detect(comp_type_dbh, fixed("branch", ignore_case = TRUE)) | str_detect(comp_type_dbh, fixed("subsidiary", ignore_case = TRUE)) ~ "Branch or Subsidiary"),
    manf_hq = case_when(
      hq == "HQ" & (manf_loc == 0 | is.na(manf_loc)) ~ "HQ Only",
      hq == "HQ" & manf_loc == 1 ~ "Manufacturing Location and HQ",
      hq == "Branch or Subsidiary" & manf_loc == 1 ~ "Manufacturing Branch" , 
      is.na(hq) & manf_loc == 1 ~ "Manufacturing Location (UC)", 
      hq == "Branch or Subsidiary" & (manf_loc == 0 | is.na(manf_loc)) ~ "Branch or Subsidiary"
    ), 
    manf_hq = if_else(is.na(manf_hq), "Unknown", manf_hq)) %>% 
  ungroup()
```


## Preparing Data Fields for Mapping


```{r}
prepare_for_maps <- function(df) {
  df %>% 
    mutate(layerId = paste(manf_hq, row_number(), sep = '.'),
                      popup = paste("<strong>Company Name:</strong>",
                                    df$company, "<br>",
                                    "<strong>Country of Ownership:</strong>",
                                    df$parent_ownership, "<br>",
                                    "<strong>Manufacturing Location?</strong>", 
                                    df$manf_loc, "<br>",
                                    "<strong>(DBH) Factory Size (SQ FT)</strong>", 
                                    df$facility_size_dbh, "<br>",
                                    
                                    "<strong>(DBH) Corporate Family Members</strong>", 
                                    df$corporate_family_dbh, "<br>",
                                    "<strong>(DBH) Company Type:</strong>", 
                                    df$comp_type_dbh, "<br>",
                                    "<strong>(DBH) Parent Company:</strong>", 
                                    df$parent_dbh, "<br>",
                                    "<strong>Address:</strong>", 
                                    df$address, "<br>",
                                    "<strong>Broad Product:</strong>", 
                                    df$broad_product, "<br>",
                                    "<strong>Specific Product:</strong>", 
                                    df$specific_product, "<br>",
                                    "<strong>(DBH) At Site Employees:</strong>", 
                                    df$atsite_emp_dbh, "<br>",
                                    "<strong>(DBH) All Employees:</strong>", 
                                    df$all_site_emp_dbh, "<br>",
                                    "<strong>(DBH) Sales:</strong>",
                                    df$sales_dbh, "<br>",
                                    "<strong>(DBH) Assets:</strong>",
                                    df$assets_dbh, "<br>",
                                    "<strong>Thomasnet Description:</strong>", 
                                    df$tn_desc, "<br>"
                                    ), 
           group = manf_hq)

}
```

We first use this function to set up our individual data layers for mapping. 

```{r}
conf_maps <- prepare_for_maps(conf_all_maps)
```

# Mapping 


```{r}
conf_maps %>% 
  saveRDS(box_here("thomasnet_totals/conf_manfs_geocoded.RDS"))
```

```{r}
conf_maps %>% saveRDS(here("/domestic_manufacturers/conf_maps_geocoded.RDS"))
```

