---
title: "Thomasnet Webscraping - Testing"
author: "Nikhil Kalathil"
date: "5/27/2020"
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This document will contain a program to webscrap and format Thomasnet search data. The results of this program are not complete and require additional cleaning/manual data entry, but this program should solve the problem of needing to download large Thomasnet searches. 


```{r, include = FALSE}
library(tidyverse)
library(rvest)
library(rebus)
library(lubridate)
library(here)
```

```{r}

box_dir <- "C:/Users/Nikhil Kalathil/Box/COVID 19 Master Folder/Data/Tests/Thomasnet Pulls/01_11_2021"

```

```{r}
box_here <- function(file) {
  paste(box_dir, file, sep = "")
}
```

# Define Our Functions

## Number of Pages

```{r}
get_pages <- function(html){
  pages <- html %>% 
    html_nodes(".page-item") %>% 
    html_text()
  
  pages[(length(pages)-1)] %>% 
    unname() %>% 
    as.numeric()
}
```


## Get Information 

There are a few key components for each entry we are interested in: 

* Company Name
* Verification 
* Location
* Supplier Data 
* Body Text

The way that the data are stored on the website means that we will seperately grab company information, verification (which will repeat company name), body text, while our location/supplier data will be joined together. We will worry about cleaning these later. 

We are going to define a seperate function for each of these components. 

```{r}
get_name <- function(html){ 
  
  html %>%
    html_nodes(".profile-card__title") %>% 
    html_text() %>% 
    unlist()
    
}

get_verification <- function(html){ 
  
  html %>% 
    html_nodes(".profile-card__header") %>% 
    html_text() %>% 
    str_replace_all("\n", " ") %>% 
    str_replace_all(" Save  Select    ", "") %>% 
    str_replace_all("Path", "_") %>% 
    unlist()
  
}

get_data <- function(html){
  
  html %>% 
    html_nodes(".profile-card__supplier-data") %>%
    html_text() %>% 
    str_replace_all("\n", "_") %>% 
    str_replace_all("        ico-map    ", "")
}

get_text <- function(html){

html %>% 
  html_nodes(".profile-card__content") %>% 
  html_text() %>% 
  str_replace_all("\n", " ") %>% 
  str_trim()
}
```


We now need to turn each of these entries into a data frame. We define a function for this as well: 

```{r}
make_table <- function(html){
  
  name <- get_name(html)
  verif <- get_verification(html)
  supplier_data <- get_data(html)
  text <- get_text(html)
  
  combined_data <- tibble(company = name,
                          verification = verif,
                          supplier_info = supplier_data,
                          desc = text)
}
```

## Clean Data 

```{r}
make_table_clean <- function(html){
  make_table(html) %>% 
    mutate(verification = str_replace(verification, company, "")) %>% 
  separate(verification, into = c("thomas_ver", "covid_19"), sep="_(?=[^_]+$)") %>%
    separate(supplier_info, into = c("loc_type", "var1", "var2", "var3"), sep = "_")
}
```

## Get Data

```{r}
get_thomas_data <- function(url, broad_prod, specific_product){ 
  html <- read_html(url)
  
  make_table_clean(html) %>% 
    mutate(broad_product = broad_prod, 
           specific_product = specific_product)}
```

## Get Data for Multiple Pages

Because the url string differs for the immediate search results and each subsequent page, we are going to define two different functions that we can use. 

If we only have one page, we can just use the `get_thomas_data` function. 

The second will be used if we have a multi-page search result. 

```{r}
get_thomas_data_plus <- function(top_url, page_url, brd_prod, spec_prod){ 
  
  #Read Main Page 
  
  first_page <- read_html(top_url)
  
  #Get Page Numbers
  
  total_pages <- get_pages(first_page)
  
  list_of_pages <- str_c(page_url, "pg=", 1:total_pages)
  
   # Apply the extraction and bind the individual results back into one table
  
  list_of_pages %>% 
    # Apply to all URLs
    map(get_thomas_data, brd_prod, spec_prod) %>% 
    bind_rows()
  }
```

## Clean Scraped Data

```{r}
clean_scraped1 <- function(data) {
  data %>% 
    mutate(loc_type = str_replace(loc_type, "ico-map Locations", "Multiple Locs, NA"),
         loc_type = str_replace(loc_type, "Custom Manufacturer", "CustomManufacturer"),
         loc_type = str_replace(loc_type, "Finishing Service Company", "FinishingServiceCompany"),
         loc_type = str_replace(loc_type, "Service Company", "ServiceCompany"), 
         loc_type = str_replace(loc_type, "Turnkey Systems Integrator", "TurnkeySystemsIntegrator"), 
         loc_type = str_replace(loc_type, "Manufacturers' Rep", "ManfacturersRep"), 
         loc_type = str_replace(loc_type, "City of", "CityOf"),
         loc_type = str_replace(loc_type, "City Of", "CityOf")) %>% 
  separate(loc_type, into = c("town", "state", "type1", "type2", "type3", "type4", "type5", "type6"), sep = " ") %>% 
  mutate(town = case_when(
    str_length(state) > 2 ~ paste(town, state, sep = " "), 
    TRUE ~ town),
    state = case_when(
      str_length(type1) == 2 ~ type1, 
      TRUE ~ state
    )) %>% 
  select(-type1) %>% 
  unite(col = "location", c("town", "state"), sep = " ") %>% 
  mutate(location = str_replace(location, "CityOf", "City of")) %>% 
  unite(col = "loc_desc", c("type2", "type3", "type4", "type5", "type6"), sep = " ") %>% 
  mutate(loc_desc = str_replace_all(loc_desc, "NA", ""),
         loc_desc = str_replace(loc_desc, "CustomManufacturer", "Custom Manufacturer"),
         loc_desc = str_replace(loc_desc, "FinishingServiceCompany", "Finishing Service Company"),
         loc_desc = str_replace(loc_desc, "ServiceCompany", "Service Company"), 
         loc_desc = str_replace(loc_desc, "TurnkeySystemsIntegrator", "Turnkey Systems Integrator"), 
         loc_desc = str_replace(loc_desc, "ManfacturersRep", "Manufacturers' Rep"))
}
```

```{r}
clean_scraped2 <- function(data) { 
  data %>% 
  mutate(sales = case_when(
    str_detect(var1, "\\$") ~ var1, 
    str_detect(var2, "\\$") ~ var2, 
    str_detect(var3, "\\$") ~ var3
  )) %>% 
  mutate(employees = case_when(
    !str_detect(var1, "\\$") & str_detect(var1, "\\-") ~ var1, 
    !str_detect(var2, "\\$") & str_detect(var2, "\\-") ~ var2, 
    !str_detect(var3, "\\$") & str_detect(var3, "\\-") ~ var3)) %>% 
  mutate(date_founded = case_when(
    str_length(str_trim(var1)) == 4 ~ str_trim(var1),
    str_length(str_trim(var2)) == 4 ~ str_trim(var2), 
    str_length(str_trim(var3)) == 4 ~ str_trim(var3)
  )) %>% 
  select(-c("var1", "var2", "var3"))
  }
```

# Webscrape

We define test kits as our end product and swabs, viral transport medium, reagents, and nucleotides as our Intermediary Product. 

## End product: 

### Covid Test Kits

Step 1: Set up URLS

```{r}
covid_test_kits_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97012798&searchsource=suppliers&searchterm=covid+test&what=COVID-19+Test+Kits"
```

```{r}
covid_test_kits_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97012798&searchsource=suppliers&searchterm=covid+test&what=COVID-19+Test+Kits&"
```

Step 2: Run Scrape

```{r}
covid_tk_raw <- get_thomas_data_plus(covid_test_kits_main, covid_test_kits_pages, "End Product", "Covid-19 Test Kits")
```
Step 3: Clean Data

```{r}
covid_tk <- clean_scraped1(covid_tk_raw) %>% 
  clean_scraped2
```
Step 4: Save

```{r}
saveRDS(covid_tk, box_here("/covid_tk_01112021.RDS"))
```

### Other Test Kits

Step 1: Set up URLS

```{r}
serological_test_kits_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=50455906&typed_term=serolo&searchterm=serolo&what=Bacteriological%2C+Serological%2C+Stool+Blood%2C+Urine+Test+Strip+%26+Virological+Medical+Diagnostic+Kits&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
serological_test_kits_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=50455906&searchsource=suppliers&searchterm=serolo&what=Bacteriological%2C+Serological%2C+Stool+Blood%2C+Urine+Test+Strip+%26+Virological+Medical+Diagnostic+Kits&"
```

Step 2: Run Scrape

```{r}
sero_tk_raw <- get_thomas_data_plus(serological_test_kits_main, serological_test_kits_pages, "End Product", "Other Test Kits")
```
Step 3: Clean Data

```{r}
sero_tk <- clean_scraped1(sero_tk_raw) %>% 
  clean_scraped2()
```

Step 4: Save Data

```{r}
saveRDS(sero_tk, box_here("/sero_tk_01112021.RDS"))
```


```{r}
test_end <- bind_rows(covid_tk, sero_tk) %>% 
  saveRDS(box_here("/test_end_01112021.RDS"))
```


## Intermediary Product: 

### Oropharyngeal Flocked Swabs

Step 1: Set up URLS

```{r}
oro_swabs_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97012641&typed_term=orop&searchterm=orop&what=Oropharyngeal+Flocked+Specimen+Swabs&WTZO=Find+Suppliers&searchsource=suppliers"
```

Step 2: Scrape Data

```{r}
oro_swabs_raw <- get_thomas_data(oro_swabs_main, "Intermediary Product", "Oropharyngeal Swabs")
```

Step 3: Clean Data

```{r}
oro_swabs <- clean_scraped1(oro_swabs_raw) %>% 
  clean_scraped2()
```

Step 4: Save Data

```{r}
saveRDS(oro_swabs, box_here("/oro_swabs_01112021.RDS"))
```

### Nasopharyngeal Flocked Swabs

Step 1: Set up url

```{r}
naso_swabs_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97012640&typed_term=naso&searchterm=naso&what=Nasopharyngeal+Flocked+Specimen+Swabs&WTZO=Find+Suppliers&searchsource=suppliers"
```

Step 2: Scrape Data

```{r}
naso_swabs_raw <- get_thomas_data(naso_swabs_main, "Intermediary Product", "Nasopharyngeal Swabs")
```

Step 3: Clean Data

```{r}
naso_swabs <- clean_scraped1(naso_swabs_raw) %>% 
  clean_scraped2()
```


Step 4: Save Data

```{r}
saveRDS(naso_swabs, box_here("/naso_swabs_01112021.RDS"))
```

### Viral Transport Medium (VTM)

Step 1: Set up URL

```{r}
vtm_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97010418&typed_term=viral+t&searchterm=viral+t&what=Viral+Transport+Medium+%28VTM%29&WTZO=Find+Suppliers&searchsource=suppliers"
```

Step 2: Scrape Data

```{r}
vtm_raw <- get_thomas_data(vtm_main, "Intermediary Product", "Viral Transport Medium (VTM)")
```

Step 3: Clean Data

```{r}
vtm <- clean_scraped1(vtm_raw) %>% 
  clean_scraped2()
```


Step 4: Save Data

```{r}
saveRDS(vtm, box_here("/vtm_01112021.RDS"))
```


### Plastics Contract Manufacturing 

Step 1: Set up URL

```{r}
pcm_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=17980004&typed_term=contract+manufactured+plastic&searchterm=contract+manufactured+plastic&what=Plastics+Contract+Manufacturing&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
pcm_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=17980004&searchsource=suppliers&searchterm=contract+manufactured+plastic&what=Plastics+Contract+Manufacturing&"
```

Step 2: Scrape Data

```{r}
pcm_raw <- get_thomas_data_plus(pcm_main, pcm_pages, "Intermediary Product", "Plastics Contract Manufacturing")
```

Step 3: Clean Data

```{r}
pcm <- clean_scraped1(pcm_raw) %>% 
  clean_scraped2()
```

Step 4: Save Data

```{r}
saveRDS(pcm, box_here("/pcm_01112021.RDS"))
```

```{r}
pcm_medical <- pcm %>% 
  filter(str_detect(desc, "medical"))
```

```{r}
saveRDS(pcm_medical, box_here("/pcm_medical_01112021.RDS"))
```


### RNA Extraction Machines 

Step 1: Set up URL
```{r}
rna_mach <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97010388&typed_term=rna+&searchterm=rna+&what=RNA+Extraction+Kits&WTZO=Find+Suppliers&searchsource=suppliers"
```

Step 2: Scrape Data

```{r}
rna_ext_raw <- get_thomas_data(rna_mach, "Intermediary Product", "RNA Extraction Machine")
```

Step 3: Clean Data

```{r}
rna_ext <- clean_scraped1(rna_ext_raw) %>% 
  clean_scraped2()
```


Step 4: Save Data

```{r}
saveRDS(rna_ext, box_here("/rna_ext_01112021.RDS"))
```

### Nucleotides

Step 1: Set up URL

```{r}
nucleotides_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=53980363&typed_term=nucl&searchterm=nucl&what=Nucleotides&WTZO=Find+Suppliers&searchsource=suppliers"
```

Step 2: Scrape Data

```{r}
nucleotides_raw <- get_thomas_data(nucleotides_main, "Intermediary Product", "Nucleotides")
```

Step 3: Clean Data

```{r}
nucleotides <- clean_scraped1(nucleotides_raw) %>% 
  clean_scraped2()
```


Step 4: Save Data

```{r}
saveRDS(nucleotides, box_here("/nucleotides_01112021.RDS"))
```

### Reagents: 

There are multiple types of reagents on TN, and as such we will have to define a slightly different procedure for handling these products. 

We start with an initial procedure of cleaning and scraping all entries

#### Reagents

```{r}
reagents_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66202367&typed_term=reage&searchterm=reage&what=Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
reagents_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66202367&searchsource=suppliers&searchterm=reage&what=Reagents&"
```

```{r}
reagents_raw <- get_thomas_data_plus(reagents_main, reagents_pages, "Intermediary Product", "Reagents")
```

```{r}
reagents <- clean_scraped1(reagents_raw) %>% 
  clean_scraped2()
```


#### Reagent Bottles

```{r}
reagent_btl_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=7060809&typed_term=reagent&searchterm=reagent&what=Reagent+Bottles&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
reagent_btl_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=7060809&searchsource=suppliers&searchterm=reagent&what=Reagent+Bottles&"
```

```{r}
reagent_btl_raw <- get_thomas_data_plus(reagent_btl_main, reagent_btl_pages, "Intermediary Product", "Reagent Bottles")
```

```{r}
reagent_btl <- clean_scraped1(reagent_btl_raw) %>% 
  clean_scraped2()
```

```{r}
reagents <- bind_rows(reagents, reagent_btl)
```


#### Bacteriological reagents

```{r}
bact_reagents_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66202409&typed_term=Reagent&searchterm=Reagent&what=Bacteriological+Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
bact_reagents_raw <- get_thomas_data(bact_reagents_main, "Intermediary Product", "Bacteriological Reagents")
```

```{r}
bact_reagents <- clean_scraped1(bact_reagents_raw) %>% 
  clean_scraped2()
```

```{r}
reagents <- bind_rows(reagents, bact_reagents)
```


#### Biochemical Reagents

```{r}
biochem_reagents_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66203001&typed_term=reage&searchterm=reage&what=Biochemical+Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
biochem_reagents_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66203001&searchsource=suppliers&searchterm=reage&what=Biochemical+Reagents&"
```

```{r}
biochem_reagents_raw <- get_thomas_data_plus(biochem_reagents_main, biochem_reagents_pages, "Intermediary Product", "Biochemical Reagents")
```

```{r}
biochem_reagents <- clean_scraped1(biochem_reagents_raw) %>% 
  clean_scraped2()
```


```{r}
reagents <- bind_rows(reagents, biochem_reagents)
```


#### Diagnostic Reagents

```{r}
diag_reagents_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66206004&typed_term=Reagents&searchterm=Reagents&what=Diagnostic+Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
diag_reagents_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=66206004&searchsource=suppliers&searchterm=Reagents&what=Diagnostic+Reagents&"
```

```{r}
diag_reagents_raw <- get_thomas_data_plus(diag_reagents_main, diag_reagents_pages, "Intermediary Product", "Diagnostic Reagents")
```

```{r}
diag_reagents <- clean_scraped1(diag_reagents_raw) %>% 
  clean_scraped2()
```

```{r}
reagents <- bind_rows(reagents, diag_reagents)
```


#### Serological Reagents 

```{r}
serological_reagents <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=96127626&typed_term=serological+&searchterm=serological+&what=Serological+Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
sero_reagents_raw <- get_thomas_data(serological_reagents, "Intermediary Product", "Serological Reagents")
```

```{r}
sero_reagents <- clean_scraped1(sero_reagents_raw) %>% 
  clean_scraped2()
```

```{r}
reagents <- bind_rows(reagents, sero_reagents)
```


#### Virological Reagents 

```{r}
viro_reagents_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=96127634&typed_term=vi+Reagents&searchterm=vi+Reagents&what=Virological+Reagents&WTZO=Find+Suppliers&searchsource=suppliers"
```


```{r}
viro_reagents_raw <- get_thomas_data(viro_reagents_main, "Intermediary Product", "Virological Reagents")
```

```{r}
viro_reagents <- clean_scraped1(viro_reagents_raw) %>% 
  clean_scraped2()
```

```{r}
reagents_full <- bind_rows(reagents, viro_reagents)
```

```{r}
saveRDS(reagents_full, box_here("/reagents_full_01112021.RDS"))
```


```{r}
reagents_all <- reagents %>% 
  group_by(company) %>% 
  mutate(tal = seq(n())) %>% 
  filter(tal < 2) %>% 
  ungroup() %>% 
  select(-tal) %>% 
  mutate(specific_product = "Reagents (All)")
```

```{r}
saveRDS(reagents_all, box_here("/reagents_all_01112021.RDS"))
```



```{r}
test_int <- bind_rows(oro_swabs, naso_swabs) %>% 
  bind_rows(vtm) %>% 
  bind_rows(pcm_medical) %>% 
  bind_rows(rna_ext) %>% 
  bind_rows(nucleotides) %>%
  bind_rows(reagents_all) %>% 
  saveRDS(box_here("/test_int_01112021.RDS"))
```

### Other Products

#### Vials

Vials

```{r}
vials_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=91782607&typed_term=vials&searchterm=vials&what=Vials&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
vials_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=91782607&searchsource=suppliers&searchterm=vials&what=Vials&"
```

```{r}
vials_raw <- get_thomas_data_plus(vials_main, vials_pages, "Intermediary Product", "Vials") %>% 
  mutate(search_product = "Vials")
```

```{r}
vials <- clean_scraped1(vials_raw) %>% 
  clean_scraped2()
```

```{r}
glass_vials_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=91790303&typed_term=vials&searchterm=vials&what=Glass+Vials&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
glass_vials_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=91790303&searchsource=suppliers&searchterm=vials&what=Glass+Vials&"
```

```{r}
glass_vials_raw <- get_thomas_data_plus(glass_vials_main, glass_vials_pages, "Intermediary Product", "Glass Vials") %>% 
  mutate(search_product = "Glass Vials")
```

```{r}
glass_vials <- clean_scraped1(glass_vials_raw) %>% 
  clean_scraped2()
```

```{r}
vials_all <- bind_rows(vials, glass_vials) %>% 
  group_by(company) %>% 
  mutate(tal = seq(n())) %>%
  mutate(specific_product = case_when(
    tal == 2 ~ "Vials", 
    TRUE ~ specific_product
  )) %>% 
  filter(tal < 2)
```

#### Pipettes and Pipette Tips

```{r}
pipettes_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=58671009&typed_term=pipettes&searchterm=pipettes&what=Pipettes&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
pipettes_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=58671009&searchsource=suppliers&searchterm=pipettes&what=Pipettes&"
```

```{r}
pipettes_raw <- get_thomas_data_plus(pipettes_main, pipettes_pages, "Intermediary Product", "Pipettes")
```

```{r}
pipettes <- clean_scraped1(pipettes_raw) %>% 
  clean_scraped2()
```

```{r}
pipette_tips_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=96164330&typed_term=Pipette+tips&searchterm=Pipette+tips&what=Pipette+Tips&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
pipette_tips_pages <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=96164330&searchsource=suppliers&searchterm=Pipette+tips&what=Pipette+Tips&"
```

```{r}
pipette_tips_raw <- get_thomas_data_plus(pipette_tips_main, pipette_tips_pages, "Intermediary Products", "Pipette Tips")
```

```{r}
pipette_tips <- clean_scraped1(pipette_tips_raw) %>% 
  clean_scraped2()
```

```{r}
pipettes_all <- bind_rows(pipettes, pipette_tips)
```
#### Vortex Mixers

```{r}
vortex_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=97010384&typed_term=vortex+m&searchterm=vortex+m&what=Vortex+Mixers&WTZO=Find+Suppliers&searchsource=suppliers"
```

```{r}
vortex_raw <- get_thomas_data(vortex_main, "Intermediary Product", "Vortex Mixers")
```

```{r}
vortex <- clean_scraped1(vortex_raw) %>% 
  clean_scraped2()
```

#### Microcentrifuges
```{r}
microcentrifuges_main <- "https://www.thomasnet.com/nsearch.html?cov=NA&heading=96001235&typed_term=microcen&searchterm=microcen&what=Microcentrifuges&WTZO=Find+Suppliers&searchsource=supplierss"
```

```{r}
microcentrifuges_raw <- get_thomas_data(microcentrifuges_main, "Intermediary Product", "Microcentrifuges")
```

```{r}
microcentrifuges <- clean_scraped1(microcentrifuges_raw) %>% 
  clean_scraped2()
```
```{r}
other_products <- bind_rows(vials_all, pipettes_all) %>% 
  bind_rows(vortex) %>% 
  bind_rows(microcentrifuges)
```

```{r}
saveRDS(other_products, box_here("/test_other_01112021.RDS"))
```


